\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersD L0006 (English)}
\noindent
Vancouver, B.C. 7/2/56
Dear Mother, well, you really managed to surprise me! But I still haven't written to you since that one card came from New York. The reason I never wrote is that I managed it, I worked up the courage. I am convinced that I won't regret it. I wished from the bottom of my heart that what she does will be the right thing. And I think I will be amazed, because I'm not getting any more replies, so I have left her in complete silence.
She also did everything in such a way that there was no other option. When we parted, she said she wanted to come along, via New York on our return journey with Fritz, "I'm coming with you." Gerda is here with me, what happens now will also interest you. About the apple trees!
Somehow a crash seems to have taken my car along with all its papers. I had a key made for \$2, since I had been sleeping in the car since our camping experience. I was just amazed, didn't say that there's no point, I sent the money for the sewing machine back with some rare letters, but rare! And we painted ourselves (on our backs) with "Souvenirs of lovely Canada." Vancouver.
Joseph has from Canada, like the ones from the USA, most of it was also real, we paid for a \$600 car. In Toronto, it sent out missionaries for a time. But no rabbis, because they still worship their gods.
The Indians are not allowed to drink alcohol, i.e., they have no license, which you need here. They are also not allowed to vote. In all states. They are allowed to enter into sales contracts and are allowed to go to high schools and are allowed in places like beaches, movie theaters, etc.; there used to be one beach for Chinese, Japanese, Negroes, and Indians and people from India. I bought a nice Indian beret, but apparently from Asians. And from Calgary also a hat like Heidi's. We listened to beautiful Heidi records at the Ochs family's house, you know, they are just like our family; the home. We often play together, they now have, in addition to the 6 children, one of the sons-in-law who has joined them, and they all fit into the circle perfectly. 3 grandchildren are already there, too. - A week from today on tour, Anne me, but without a tour. San Francisco, then past Mount Whitney (4495 m, highest mountain, not 50 miles further is the lowest point in Death Valley below sea level), then Boulder, America's largest dam, Grand Colorado, then to the Mexican border. From there, depending on the time, maybe via Florida. It's so Friedrich doesn't drive alone. How are you all? Friedl has too much work. I'm sorry that we can't come visit you, but maybe we'll do it next year.
\end{document}
