\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersE L0006 (English)}
\noindent
Toronto, December 26, 1955-

Dear Mutti!
I'm working a "split" shift all week, which means I have off from 1-4. That's practical for writing letters.
First of all, many thanks for the Christmas package. The anorak fits great (only the sleeves are a tiny bit too short, but that doesn't matter). I'm very happy with your Jogg! A belt might not be a bad idea, since it's quite wide. The cuffs are nice and tight, and the jacket isn't heavy, even for cooking. The idea with the soap bag is great! Nobody here has anything like that, and I can now take it to the cottage in the summer or when I go swimming. I got a very loose pair of pants from Inge; maybe I can still use them to sew the dirndl that I don't wear anymore. I can really use everything so well. Grandmother gave me a book written by an Armenian woman, with very humor-filled pictures. Aunt Anni gave me a book about the Alps with lots of photos, along with a market bag that I really like, it's just great.

Klaus gave me a wristwatch; mine has been broken for 5 years, and now it feels very strange to have a watch again. Many thanks also for the gift certificates; we used them to bake butter cookies, cheese and bread, and fruitcake. Our Christmas tree this year is much bigger and more splendid than last year; it's a magnificent piece. Freden took pictures yesterday, so you will see many pictures soon.

On Christmas Eve, after church, we all went to Inge's: Manfred, Siegfried, Heinz, Joe, the Edland sisters, and me. Since we were all very hungry, we ate first—potato salad and sausages, as much as everyone wanted. Joe, our big eater, consumed only 16 sausages. Then we lit the Christmas tree, meaning we plugged the lights into the socket, and then we sang some Christmas carols. Since there were so many of us, we then played party games, drank coffee, listened to records, and laughed a lot. There were also all sorts of pastries and cakes, of which everyone had plenty.

On New Year's, the men will be serving us food, 16-18 of them. We'll see if they can cook. You'll be able to see that in the photos. Freden got a new camera for Christmas and now he wants to buy a Retina so he can take color pictures. I gave Inge a color box of Herbert's paints, the kind where you press a button with your foot and the lid pops open, and for the little ones a small box with all sorts of baking things, a cake for the dollhouse, and for him the same thing you gave him.

On January 4th, night school starts up again; we had two weeks of vacation. Now it's 10 weeks long. Then all the students will work, in a factory, in a hospital, as a waitress, which is why the factories and hospitals are also very happy to give vacation time. And Lise is in high school. And what a university is. Otherwise, you don't choose your own subjects, but rather according to the school year, and math and history are required subjects. You can then choose a certain number of electives, for example, physics, typing, bookkeeping, home economics, and for boys, practical classes like metalworking. If you don't pass a subject, you don't have to repeat the year because of it, but you just take that subject again and try to catch up. If not, you just can't take your final exams in that subject, if it's an elective. So you might be in grade 7 for math and in grade 8 for everything else.

We are already starting to decorate our apartment. We're celebrating New Year's at our place, so we have to make a decent portion of Italian salad and sausages for all the guests. And goodness, without a lot of vinegar and onions, because they'll be drinking alcohol. We're making a hot punch. They have to drive and be ready to go skiing at 8:00 in the morning.

Best if I send it, or not? That's the most likely way, isn't it? Do you know if Uncle Max is only on a trial basis, besides the trip of course? It would be nice for a while. Then he could stay with us. But I'm not sure at all, and I don't want to...

Warmest greetings and all the best,
wishes your
Sisi
\end{document}
