\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{L0007 (English)}
\noindent
Way 31st May 3/4 7 ne! VI

Dear Mother, last night we skipped writing, so I'm finishing the letter now.
That business with the arrangement is a stupid story, how on earth did you get involved with it? Is the grocer not going to take anything in the summer now? That is certainly a loss. I'll send you P 60 the day after tomorrow, because I want to be completely debt-free with you, and I've already been debt-free with you both for two weeks, which is a wonderful feeling. As soon as I can, I'll send you money, but in the next few weeks I'll need quite a bit for 3. C. I'll think about what the best thing to do is.
The ski area wasn't the only thing, but as I said, we had a decent run. Next winter we'll start skiing earlier. The gymnastics was at the night school.
With the color film, it's terrible that nothing came of the 24 DM. Who took those pictures anyway? But do send me the slides sometime, or what happened to the film? Did the ones from Niagara Falls not turn out? 24 DM is an insane amount of money, even for me.
By the way, I'm not surprised that there was nothing on the other two rolls of film, because they were new. They were actually black-and-white reversal films that I wanted to slip to the Cläfin because I want to make color slides. All of this together has turned into an expensive bit of fun, for which I'd at least like to have the film, because the falls were one-of-a-kind back then.
The alarm clock is working perfectly, I'm so glad I got it. Of course, I always place it pretty far from the bed, but that way I get up and out without a problem. If I don't, I just sleep right through it.
My watch, the one from your ad, is broken. I took it to the shop; hopefully I'll have it back soon.
Next Monday I have to go to the dentist. I broke off a filling four weeks ago, which is a real mess. First of all, I would have stayed loyal to Dächle, and second, they are so outrageously expensive here.
I might buy an enlarger that can also handle 6x6, because a good friend of mine bought a Rolleiflex. I've also already taken passport photos for Siegfried, and the other night I have to take some portraits for an acquaintance.
Well dear Mother, now I must hurry off to the hospital,

I'll soon get some tablet fertilizer for the Opielien again, tested by me, I also recommend it daily.
\end{document}
