\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS1965 L0002 (English)}
\noindent
Bauff, Jan. 9/65

Dear Änneli,
Yesterday the two parcels arrived, and finally the teddy bear and shoes for the children, too. Even though I was already quite annoyed, it still made everyone very happy, and everything has arrived now. You sent so many parcels that for a while it seemed like it would never end.
Then every company also sends special offers (like a catalog, just any kind). Here, you buy from a catalog. You might be asking yourselves: how do the poor people manage that? Well, I want to ask the poor myself, since for those who didn't live through the war years, it's not hard at all. Today another little parcel went off to the front as a small thank you for the tears.
Tomorrow Uncle Fritz has already taken time off for the cinema. The Beatles, of course! I was delighted, as I got to see a performance of Frangoisadeline with the false beard. Later, I'll be at home crafting and sewing. But for now, please send your charming mail again, and I will paint a little bird bath in an eggshell. Hopefully, it will get more beautiful every day. Yesterday, All Geuter and one of his new ones were up all night, so that a gentleman from Vancouver is coming to Bern, provided that, of course, they don't have to write about the waterproofing.
Another party, and the celebration should finally come to an end.
Whatever the case, it is lovely. They visited the children yesterday, but nobody was home because I was out.
Yesterday I finally visited Aunt Annelis. Then a call came promptly from Aunt Annelis, saying they were all alone and that I hadn't been seen in a long time. I hadn't had any time until now, because I always had the children. But it was very lovely and cozy there.
On March 7th or so, Aunt Käthi might be coming, so I can send a few things then. It's no wonder that it takes so long, since it has to cross the big pond. That takes an eternity.
Yes, you ask about the children. All the little ones are doing well and are healthy.
I also sent special greetings to Aunt Greth, and with Uncle Röth, there's also so much going on, and it always seemed to be a birthday. For Annelis' birthday, there was the most beautiful sunshine, and the war years are over, etc. We were also glad when the whole thing was supposed to suddenly come to an end.
Soon it won't be so bad anymore.
Yesterday Sylvelin Balen, who was introduced yesterday, we had... but it's back to where one every morning
\end{document}
