\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS1962 L0003 (English)}
\noindent
Vancouver, Nov. 15/62

Dear Mom,
Thank you so much for your letter. I can hardly wait until Christmas for the package to arrive. The little baby things always look so sweet. It's especially nice of you that you want to give us the carriage as well. Eric has already started on the little crib; he's enjoying it. I was in Banff last weekend and saw the apartment for the first time. Erna is already living in it. Since it's not so easy to buy land in Banff at the moment, we have to wait a little longer. But we have rented half a house, that is, with its own entrance and completely self-contained for us; they call it a duplex here. We have a living room, two bedrooms, a kitchen, and a bathroom. That way we can put the little one in its own room, which is much better. It's all not very big, but there's still enough space for potential overnight visitors. We'll surely get a lot of ski visitors from Vancouver, and in the summer many friends, too, who will be glad to have a place to sleep. Behind the house stand about 20 huge, old fir trees, and the deer and elk come right up to the kitchen door. At night, however, bears also show up now and then. The other day one knocked over the new garbage can. Now we also have to buy furniture. For now, Eric is building a bench in the living room, and I'm making foam rubber cushion covers for it. It will be so big that it can be used as a bed. Eric has also already bought two wicker chairs and two dressers for the bedrooms, and then we still need a refrigerator and beds and two chairs for eating. I have a table, and we'll build the rest bit by bit. The reason I'm writing in a hurry is to ask a favor. For Christmas, I would like to give Eric a pair of knickerbockers, the same kind I received. The tag has the size and the measurements in inches. Maybe you can convert that. I would be so grateful if you

could send them, because they don't have them here. Thank you so much for the well wishes. an undergarment suit, from old ones used by the fathers and passed down again and again. It is very light and warm, and I thought, sewn together like the rubber pants, lined against [?] the cold, You can also stick them in your pocket when you are on the pot. Or you can also just wear them like that, I am not at all angry if siblings get one like this because they get one. So far I could always send a food parcel late. I also hope that they also get a little less than usual, but when you see the children for weeks you do them with... when they have a little less than I... the suits only in warm wash eats, also dye if you want washing powder, with warm.
In case I don't get a chance to write again, I'll wish you a happy New Year now.
Warm regards,
Your Dale

Thank you for the baby things.
Both looked at them, then I put them
back under the Xmas Tree. They are
very nice. Now I wish you a
Xmas \& a very happy New Year
all.
love Eric
\end{document}
