\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersK L0007 (English)}
\noindent
H. David Dec. 5, 1957.

Dear Mother, for Christmas and the New Year, I wish you all the best and as few worries as possible. At least this year at Christmastime, you won't be so completely alone, since Christel is with you. It's lovely that she likes it so much there and is having a lot of fun with the children. I must say, when I left, I was very sad that the children weren't there, since we don't do that much on our own. But the children aren't so little anymore and need to see other things sometimes. But now for the most important thing I wanted to write to you: a few days ago, the other girl arrived, the one who was actually supposed to come in the spring. She is from East Prussia, is 24 years old, her name is Ruth, and she is very nice. She is also very tall and strong, so she can really get some work done. She is staying with me over Christmas and is also allowed to go out from 6-8 o'clock and then come home, as she has relatives here. She is completely free on Saturday and Sunday. On Christmas Day, she will be having dinner with her relatives. So it's really quite good that she is here. She is also very neat and clean. She has also worked in a guest house before. She gets the same pay as Christel. I must say, I am very pleased, because Christel is still very young and inexperienced. She still needs a lot of guidance. So, now for something else. I received your letter and was very happy. I also got a letter from Aunt Frieda. She writes that she can't come because she isn't feeling well. She also wrote that she is very happy that Christel is with you. She wants to come and visit you when she is feeling better. I also got a letter from Aunt Martha. She writes that she is very happy that Christel is with you. She wants to come and visit you, too.
\end{document}
