\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{L0005 (English)}
\noindent
Toronto, 12/26/55

Dear Mutti,
I'm working a "split" shift all week, which means I have off from the 1st to the 4th. That's handy for writing letters.
First of all, thank you very much for the Christmas package. The anorak fits perfectly (and the jacket is great too), we are doing very well. I find the elastic practical, it keeps the draft out. The belt is perhaps a little wide, but one always adjusts it. The neighbor is also great. What an idea! Because here has my... something like that, and also for summer in the canoe or to the beach is now a flawless... Yes, I was very happy, thank you again, very, very much. Also for the cake. It tastes... a gift from an American. Humor as well. A letter came from Aunt Elsi from the Alps with many photographs, from Fredi the postcard, which you saw, it's really great.
And Klaus gave me a wristwatch, and from Inge I got a flawless watch chain, now I can choose which one I should take. And everything else is good too. Brenden was thrilled, he got a book about airplanes. Mine has been broken for 5 years, so it's quite strange to... again, a watch to... Thanks and for the vouchers, we have... our wristwatch gift... also baked, butter cake, cheese bread and Kuntzelbrot. Our Christmas tree is much younger and fuller than last year, he took pictures yesterday. Yes, pictures, pictures... want...
On Christmas Eve, after... we all went to Inge's, Manfred, Siegfried, Heinz, Joe, the Edland sisters and I. Since we were all very hungry, we ate potato salad and sausages. Joe, our... caramelized the sausages. Then we lit the Christmas tree, that is, plugged in the lights, and sang Christmas carols. Then we played party games, drank, listened to records, and laughed a lot. At midnight... still... then to go home the next morning.
On New Year's we will celebrate New Year's Eve with us, 16-18 people, 'mal see the boys sleep. That can... Elliger, Hilde Köcher... has also written how now in her... employed by the U.S. Air Force, and there also at the Rotary Club... days there at the program of a project... got as a gift, now he wants to do something like that this year... is a magnificent piece.
Then you will... has only 16... with... and all coffee... everyone so much... put in... places in... spruce... had... and old coffee... several games... will be an event and ends on the next... makes at... on the next... essentially... on Christmas... one, the... also in the... camera... buy a Retina so she can take color pictures. I gave Inge a paint box (Herbert's paints/watercolors), so that she only has to press a button and the lid opens, and for the little one a box with 12 thick, round children's paints.
As you already know... on 1/4 evening school starts, we had 2 weeks of vacation.
It is above all the big vacation, because it's 10 weeks long. Then the children from all the schools go to work, in factories, in hospitals as waitresses, which is why the factories, hospitals and others also have a longer... in the summer, because there is enough temporary help then. Otherwise, high school is like a university, you choose your own subjects, especially after the first 2 years.
And... is a required subject, then you have to choose a certain number of other subjects. Such as, for example, world..., physics, chemistry, languages, typing, shorthand, home economics, for boys also practical classes, orchestra. In... year will... otherwise like work, if you get through it you don't have to repeat the year... others do this subject again... takes... with, gets help for the... and tries to catch up. If not, you can't get your diploma in this subject, if it's an elective. So you might be in grade 7 for math and in grade 11 for everything else.
We are already starting to decorate our apartment. We are celebrating New Year's at our place. Since we are only making a tiny portion of Italian salad and sausages, and of all good things... we will make a little alcohol or drink. We'll make a hot punch, and good for driving the car.
8 or 12? in the morning to go skiing.
I should write to Uncle Max sometime, because he can tell me whether he... or the grandfather... It's best if I send him a letter, or not? Or is it really best to wait until Uncle Hans is back? You know, if Uncle Max were only on a trial basis, besides the travel of course, if... nice for a while. Then they can stay with us, with a tent or something. But I am quite... and I would first like to...
Warmest greetings and all the best,
wishes you
Your
Numan-Josh
\end{document}
