\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersA L0007 (English)}
\noindent
Vancouver, Dec. 30,

Dear Mother,

I just got home from work and the package was here. I thought it would still be sent to my old address, so I wasn't at all prepared to find it here. The sleeping bag is really great, so light and small. I'm going to try it out and sleep in it tonight. I have so much room in it that my head fits inside too, which is practical. And the crampons are so nice and light, and they came with the practical carrying frame. I'm already looking forward to the ice hikes in the spring and summer. I've had the hut slippers on all evening, but that's a good idea to wear them inside the sleeping bag. Plüschke will surely find his spot in my cozy corner soon. I built myself a nice bookshelf out of boards and bricks, a corner unit, which also holds my radio, record player, tape recorder, and typewriter and sewing machine. I really should be home a bit more, it's so cozy. The clapper is hanging there too, and the recorder, heather, and pretty pictures. I'm always so happy about the pretzel sticks; I'm more of a savory person than a sweet one. And the fir branches smell absolutely wonderful. They're shedding a little, but are still quite green. Are they from your Advent wreath? Imagine, after a long time, I got another long letter from the Bitners in Fairbanks, Alaska, the people I traveled to the north with back then. That made me very happy.

On Christmas Eve, I was with Gudrun and George and Franki. The little fellow was just adorable; he'll be one year old on January 3rd. I'll send you pictures from Christmas and also from Toronto, I just couldn't get any photo paper. The four of us had a nice celebration. On the 25th at 6 in the morning, we set off to go skiing. We had absolutely wonderful weather over the holidays, sunny and cold with powder snow. There's about 1 1/2 to 2 meters of snow now. I'm enjoying skiing more and more, now that I'm getting better at it. But I'm also lucky that I get to ski with the best skiers in the West, and 5 of them are ski instructors who teach you a lot for free. We slept in the car the first night. It was nice and warm. The second night, we slept in the cottage of some acquaintances, which is right next to the Selbs Lodge. Do you know what Sue Fry sent me from England? She's one of the Australian girls, the quiet one with the straight hair. She sent a Christmas card with a color photo of you, Christel, and Bärbel sorting apples. That was a very nice idea, I was so happy about that. The three of them are working in England now, in London, which they don't like as much after beautiful Vancouver. My friend Wilma, also Australian, is going to Germany next year, to Lake Constance, and is looking for work as a domestic helper. Would you perhaps want to have her? She would like to learn German and can already make herself understood quite well. In the winter, though, she wants to go skiing every weekend. She's 21 and just got her driver's license.

Who knows, maybe it will work out for me to come for a longer vacation in 1961, to help out as well. I haven't heard anything from Ursel since Easter, apart from a few postcards from her trip out West. I don't have an address, have no idea what she's doing. Please, write and tell me her address soon. What's going on with her? I would like to help her.

It's terrible that Medri always has headaches. Yes, I know how well off I am to have been so healthy so far. My head doesn't hurt, nor my feet or my back, and my bad eyes are so bearable for me when I think of Christel or Ursel. My teeth aren't exactly in brilliant shape either, but these are all such minor things. Sometimes I think it's a little unfairly distributed among us siblings, with Ursel and Christel being at such a disadvantage because of their eyes.

Over New Year's we're going skiing again for 3 days; it's wonderful every time to drive up from warm Vancouver into the snow. We are all completely sunburned from the wind and sun. We never have enough money for the chairlift, so we let ourselves get pulled up by the rope tow, for a whole day at first, and you can really feel it in your arms afterward. I don't think they even have rope tows like that in Germany. You hold on to a rope and ride up the mountain on your skis at a breakneck speed. It really takes a toll on your arms, and in the evening we are properly tired. Then we cook in the ski wax room and crawl into our sleeping bags and sleep for 12 hours, get up at 8 and are back on the slopes after 9.

With my tape recorder, I've already recorded a lot of nice tapes, so I don't need to buy records anymore, but instead fill up my tapes with beautiful music. Above all, I already have a wonderful collection of English, Canadian, American, and Australian folk songs. One hears a lot of beautiful records again during the holidays.

Hopefully you can make use of the blanket. I thought, when it's so terribly cold, at least to warm up with. Unfortunately, I was given the wrong information about the electricity. Were you able to get a transformer?

We've rented a cabin to celebrate the occasion. Otherwise we always sleep outdoors. We always drive to the next campground. There's a covered fireplace with tables there. We lie down on the tables and are nice and warm. We really enjoy it when the wind blows around our ears and the night birds cry and the river rushes. I brought my books with me from Toronto, so now I have a nice big bookshelf full of books in my room. Are you actually a member of the book club? I would have liked to send you pictures, but I haven't developed them all yet because I couldn't get the paper. They will follow. Hopefully you will use the electric blanket. They told us at the store that it would work for any current, but it's 110 volts. You'll need a transformer for that wattage. Can Christel get one for me at my expense?

Very merry Christmas greetings,
your Onkel
\end{document}
