\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersG L0002 (English)}
\noindent
Toronto, Feb. 24, 55

Dear Mutti!
I want to apologize for my letter. I'm sorry, I was indeed thinking too selfishly. I certainly won't do that again. It may well be that I did everything rashly back then. One just shouldn't send off bad or unpleasant things right away, but rather wait until everything has cooled down a bit. I didn't know that my Christmas letter, which I sent before Michi's, didn't arrive, so please forgive me again. Please don't dwell on it, if it was colder without the Eber boys. And when I suggested back then that you all might want to come, it was because it would have been easier for me, not because I had a guilty conscience about it, since I had actually promised to come back. I had been firmly resolved to do that back in Germany. I also enjoyed my time at the Sitzels' without working outside, and by the way, I still do today. What can I do if I like it so much here? In the beginning, I fought against these thoughts often enough \& we still haven't seriously discussed whether it's advisable for all of you to come over, other than calculating how quickly we could have a house. I'm not trying to persuade Mochi either, simply because she knows you all better. I don't think she has ever seriously considered it. I think she's already quite confused. She is really adapting tremendously, almost too quickly. 1 1/2 years is almost too long if one plans to go back and continue living over there. I believe, or have the feeling, that for her, 1/2 a year would be the absolute limit. She bravely tells herself that she would never stay here and will definitely be in Germany next spring. Just don't think I want to get rid of her, I just mean that it will be very difficult for her

to readjust again, also to German circumstances, and an adjustment to more Rhenish circumstances is much more difficult. But let's hope for the best. We enjoyed our ski trip very much. Me too. It was also wonderful. We had snow and sun, unfortunately only 4 pairs of skis, so I hardly got to ski at all. And when there were skis available, my ski boots were in use, since several of the girls didn't have boots. In the evening we had a costume ball, which unfortunately turned out to be pretty lousy, since most of them had sore muscles and were tired from all the fresh air. But the next day at noon, before we left, we had another nice dance. The ski instructor and his wife were also there, which was nice when we sat around the fireplace in the evening and sang while he played the guitar, that was a really great atmosphere. We sang many of those songs with a chorus, where one person sings a solo; "Stumpfsinn, der mein Vergnügen," and "Schön ist ein Zylinderhut" etc. But also beautiful folk songs. The ski instructor is going to build himself a cabin up there in the summer. We took nice pictures, mechi has already developed some of them. Starting today, mechi is working overtime at the hospital, so she'll be earning really good money, which is great. She now works from 4:15 - 7. She also earns quite a bit from the pictures. I'll also be happy when she has paid off her debts, not because I need the money, but it is getting to be a bit much. She has paid off her enlarger; I think she has already paid Ehr off herself. She certainly won't regret the purchase. What I find a bit more unnecessary is that she now wants to buy skis for \$18, but that's her own business. I don't think anything will come of our vacation to B.C., which is a shame for Mechi, although it might have been almost financially impossible for her. With the loss of work, it would have come to about \$150. So we'd like to go to Nova Scotia and I'll go to the north, that will certainly be very nice too. Inge will also come along, Mechth is not very enthusiastic about that, but that does happen more often, that you get along better with your wife than with your sisters, especially since we did a lot together last summer. Next week we're going to the opera, "La Traviata." On March 3rd we're invited to Uli's birthday party, 12 from our group, we want to give him an air mattress or a sleeping bag, you can really use that on camping trips. Inge and Hilde are already over the moon, their mother is coming by plane on Good Friday and staying for 7 weeks and will then travel back to Germany with their father. So today they bought a couch and built a tea table; they got the money for it back from overpaid taxes. That's certainly more pleasant than my situation last year, when I had to pay an additional \$42. I recently saw "Désirée" here with Marlon Brando, it was good. But "On the Waterfront" (Marlon Brando) was even better; in Germany I think it's called "Die Faust im Nacken."

fired. Last time we glazed some of them, now they will be fired again. Because when the glazes are wet, not fired, they look red, and then they turn light green during firing. It's like with reversal film in photography. We still enjoy sports a lot, Mechi now goes twice a week too. Afterwards we always go swimming. It was Mechi's first time in an indoor swimming pool on that occasion. When I had the late shift and didn't get home until 8? o'clock, Mechi always had cooked for me, but now she's getting better and better. By the way, Jenny wrote to me that Mechi looks so angry in the picture I sent once. That's because it was taken at the Santa Claus parade. Mechi was snapping away, and then she wanted to change the film and the film in both cameras had torn, so she was angry, she doesn't just look that way.

Regards, Dorli.
\end{document}
