\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersJ L0001 (English)}
\noindent
Opr. 27
St. Catharines, April 27th

Dear Mother,
I wish you a very happy birthday and hope,
above all, that you have many worry-free hours. I'm sorry
that I wrote to you about shortages in my last
letter. I will come back again,
as I promised. In the meantime, I'm going to see
as much of Canada as I can.
Even if I'm not always working in
agriculture, it's not wasted time.
But I was surprised that you think of the
earnings when it comes to a profession! I found that
unusual. Apart from that,
nurses here are very well paid and there
are always positions open. With this plan,
I also thought a lot about the future, perhaps precisely
for a situation that you might one day find
yourself in. A three-year course would probably
not have been an option anyway, since you need a high school
diploma, but only a 9-month course,
during which you would still earn nearly
as much as in domestic work. I might
still do that someday. At least the food is good.
How is Ursel? Was she also in Bern-
bach? I wrote to her in Tübingen once,
but as expected, I didn't get a reply.
Have you heard anything from Erdmute?
She wrote to me a couple of times
last year, but I didn't get an answer to my
last letter.
It's still not spring yet. But when
it gets warm now, the apricots
will probably bloom soon. On my days off,
I always go to the farm to do some
weeding, since everything is grown flat
along wires. The asparagus harvest has long
since begun in the south, but not here yet. Have
you planted the lettuce? Fertilize the animals
well, it tastes sweet as sugar. Here, "sweet"
is used for anything that isn't explicitly
salty or sour. For example, unsalted
butter is "sweet butter." How are the assistant
and the apprentice doing? The radio just announced
snow for tomorrow.
When will you give a sign again? We
used to always do that on your
birthday.
Warmest greetings to you all
from Joch.
\end{document}
