\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{L0006 (English)}
\noindent
Dec. 26
1955 Toronto, 12/26/55-

Dear Mutti,
I'm working a "split" shift all week, which means I have off from the 1st to the 4th. That's convenient for writing letters.
So first of all, thank you very much for the Christmas package. The anorak fits perfectly, we like it very much. I find the elastic in the belt practical, because you always need to pull the coat together, but not too tightly. The cuffs on the sleeves are also very good. I also baked, butter cake, cheese bread, and Kuntzelbrot. Our Christmas tree was bigger and, we hope, better than last year; it's a magnificent specimen. Gersten took pictures again, so you will see a lot of pictures soon.
On Christmas Eve, after church, we all went to Inge's place: Manfred, Siegfried, Heinz, Joe, the Edland sisters, and I. Since we were all very hungry, everyone ate as much as they wanted: potato salad and sausages. Joe, our big eater, consumed only 16 sausages. Then we lit the Christmas tree, that is, we plugged it in, and we sang Christmas carols and then played party games. We drank, listened to records, and laughed a lot. The next morning, however, everyone was ill.
On New Year's we will be eating outdoors, 16-18 people, we'll see if we go to bed the next morning. You wrote that we are allowed to send you pictures of how you are enjoying yourselves in your U.S. and that our Bardeschen Club is also enjoying the cheerfulness of youth there. Now for Christmas I would also like to buy a Retina camera so that she can take color pictures. I gave Inge a color box from Herbertsmaler, one of those where you press a button with your head and the lid opens, and she also got a tripod for small things. For myself, I was given a youth group calendar. We had wanted one for a long time.

On January 4th, night school starts again; we had two weeks of vacation. Now it's getting serious. In 10 weeks, half of all the students will go back to work, in offices, in the factory, as waitresses, and elsewhere. That's why the factories, hospitals, and all employers are very happy to have people take their vacation in the summer, because then someone from the high school is there to help out. A university student chooses their own subjects from the semesters, and mathematics and history are required subjects. Then there is a certain number of subjects you can choose as electives, for example, physics, typing, bookkeeping, home economics; for boys there are also practical classes like lathe work. If you pass, you move on, but if you fail, you have to repeat the subject. If you still can't manage it, you can't get your diploma in that subject, if it's an elective. So you might be in grade 7 for math and in grade 12 for everything else.
We are already starting to decorate our apartment; we are celebrating New Year's at our place. So we have to make a decent portion of Italian salad and sausages, because without alcohol, they will get thirsty. We are making a hot punch, and for the car ride, we'll have a hot punch, and we'll be heading out at 8:00 in the morning to go skiing.
I'll send the photos to Uncle Max, because he can't come see them. The best thing would be for me to send them to Uncle Hans, right? That's the most likely place. Do you know if Uncle Max is only here on a trial basis? Aside from the travel, of course, that's already a lot for a while. But I'm quite sure about it.

Warmest greetings and all the best,
Your
Numan-Josh
\end{document}
