\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS1965 L0006 (English)}
\noindent
Vancouver, 6/13/65

Dear Mutti,

it has now been 60 weeks that Eric has been working and the children and I have been living in Vancouver. A year has gone by. The first half is definitely it. When we consider everything that has happened during this time, the time hasn't passed so quickly after all. The first year is definitely the hardest. Everything is much easier now. Everything has fallen into place. The children are doing well in school, Eric has settled into his job, which wasn't easy, because the work is not only new, but also the language. I have gotten used to the house, learned to drive the car, and familiarized myself with the local way of life. It's not perfect yet, but it's wonderful, to the point that one can now enjoy the beautiful sides of the country.

Now, old worries my path- One thing such big worries for several weeks already, and one or two months, or two winters should be in operation, it now looks as if something outside- telephone booth, which stands painted with filth. That on the hell and coals all workers but still paid, much more than the community gave them for the work. So we want to continue to fight for money for a month in the old house, which is a department and all occupied with files. Three days or four days without electricity. The threatening letters from Vancouver, after three weeks came from Fahrenheim, constant complaints, which they however paid to Zebe, the mail with this delay, otherwise very good. It with a complete and without interruption, only now and then free swimming, which went from Vancouver to the baths, and a particular station, which is illuminated by a picture. It is the parents at every spot, every fountain, one talks a little bit, that is a basis for a small-red-white flag from the old mining tunnel. Soon a little lie in calm warm water.

It is very disturbed, helicopter noise, airplane, a restaurant is being
\end{document}
