\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersE L0004 (English)}
\noindent
Toronto, 26.12.55-

Dear Mutti,
I'm working a "split" shift all week, which means I have from 1-4 off. This is very practical for writing letters.
First of all, thank you so much for the Christmas package. The anorak fits perfectly (only the sleeves are a tiny bit too short, but that doesn't matter). We are doing very well. I am now very happy with your jacket! A belt might not be a bad idea, since it is quite wide. The cuffs are nice and tight, and the jacket isn't heavy, so it's good for cooking in, too. The idea with the beach bag is brilliant! No one here has anything like it, and now I can take it to the cottage or to go swimming in the summer. I got a very loose pair of pants from Inge; maybe I can still sew the ones I don't wear anymore. I can also use everything so well.
Grandmother gave me a book written by an Armenian woman, with very humorous pictures. Tante Anni gave me a book about the Alps with lots of photos, along with a market bag that I really like a lot, it's just great.
Yes, I saw it, and a jacket.
And Klaus gave me a wristwatch; mine has been broken for 5 years, and now it feels very strange to have a watch again. Thank you very much for the gift certificates; we used them to bake, butter cakes, cheese \& bread, and a delicious fruit bread. Our Christmas tree this year is much bigger and more splendid than last year; it's a magnificent specimen. Vreden took pictures yesterday, so you will see lots of pictures soon.
On Christmas Eve, after church, we all went to Inge's—Manfred, Siegfried, Heinz, Joe, the Edland sisters, and me. Since we were all very hungry, we ate first: potato salad and sausages, as much as everyone wanted. Joe, our big eater, devoured 16 sausages alone. Then we lit the Christmas tree, that is, we plugged the lights into the socket, and then we sang some Christmas carols. And we sang against each other, because there were so many of us. Then we played party games and drank old coffee, listened to records, and laughed a lot. There were also all sorts of pastries and cakes to eat, of which everyone had plenty the next morning.
On New Year's, the men will be serving us food, 16-18 of them. We'll see if they can cook. You'll be able to see that in the photos.
We're not allowed to write about how poison gas weapons are now being produced in the U.S. There at the boarding house club, there are significantly more people on the weekend. We did a project for Christmas and because he got a camera as a gift, he now wants to take proper pictures. Now he wants to buy a Retina so he can take color pictures. I gave Inge a color box from (Herbertsmalerei/Herbertsmalfarben), the kind where you press a button with your foot and the lid pops open, and for Uleins a little box with all sorts of baking things, a cake for the dollhouse, and for him the same thing you got him.
On January 4th, night school starts again; we had two weeks of vacation. Now there are 10 weeks of it, especially the big vacation days. Then I'll work all school hours, in a factory, in the hospital, as a waitress. That's why the factories and hospitals are also very happy to give vacation time up there. Yes, and Lise is in high school. Yes, and what a university is. Otherwise, you don't choose your own subjects, but rather according to the school year, and math and history are compulsory subjects. Then there's a certain number of subjects one can choose, e.g. as electives: physics, typing, bookkeeping, home economics, and for boys, practical classes like metalworking. In every class, you do work like that. If you don't pass a subject, you don't have to repeat the year because of it; instead, you just take that subject again with everyone else, get extra help, and try to catch up. If not, you just can't take your final exams in that subject, if it's an elective. So you might be in grade 7 for math and in grade 11 for everything else.
We're already starting to decorate our apartment. We're celebrating New Year's at our place, so we have to make a decent portion of Italian salad and sausages for all the guests. And my goodness, without a lot of vinegar and onions, because they will be drinking alcohol, or we'll make a hot punch. They have to drive and be ready for skiing at 8:00 in the morning. A shame Onkel Max will scold him once.
The best thing is if I send him, or not? That would be the soonest, right? Back to Onkel Hans? You know, if Onkel Max were only here on a trial basis, apart from the travel, of course, that would be nice for a while. Then he could stay with us. But I'm quite sure, and I would like to, but it's not possible.
Warmest greetings and all the best,
wishes you
Your
Sisi
\end{document}
