\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersA L0003 (English)}
\noindent
Vancouver, May 20, 59

Dear Mother,
Thank you so much for the birthday package. As you can see, I'm already making good use of the ballpoint pen. This is certainly a better way to write than with a "Kugel." I didn't even find it at first among the wood wool, and it was only last night when I was clearing away the packaging that I found the little skirt. That was quite a surprise. I took the pretzel sticks with me up the mountain for skiing, and everyone was thrilled with them; they disappeared very quickly. The cards have also been broken in, as it snowed so hard on Sunday that we couldn't go skiing. So we played Canasta instead. The rules for Canasta were included, did you see that? We've been playing it here for years. It's much more entertaining than "Kommiss," for example. Christel's rain cape was a really thoughtful gift for this place, since it rains so much here it's not even funny anymore. This year the spring has been especially rainy and cold. It's a good thing we're never in Vancouver over the weekend. The ski season is coming to an end, but we're gradually starting to look forward to summer and hiking and sailing and canoeing. When I think back to 2 years ago when I was here, everyone said you couldn't go up into the mountains because there were no trails, no huts, no trail markers, and lots of bears. And yet you can go everywhere, it's just not as easy and comfortable, and the bears are usually not dangerous either, except for the grizzly bears, and they are quite happy if you just leave them alone.

We're getting a brand new, modern bank in the summer, on the next corner. That will be fun. I am now the Head Teller there, which is also simultaneously the supervisor for the rest of the employees. Liesel writes that she's not at all sure if anything will come of her trip out west. That would be a pretty strenuous drive, too, if they aren't used to driving on such long roads! The Freude girl has apparently already failed her exam a couple of times. It's nice that Liesel is at least working a bit more in her field now. That photography course must be interesting. I could probably slide into the photography business here too; I know several people who could get me in. But I don't know. Here it's all just lab work, unless you're a really good photographer. A lot of it is already so
\end{document}
