\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{L0001 (English)}
\noindent
Toronto, July 20, '55.

Dear Mother!

I'm sure you've all been waiting for a detailed report of my trip, and now, here it is at last. To put it briefly, it was magnificent. I saw so much of Canada that I have a completely different impression of it now. But I want to tell you everything in order. The reason I haven't written again is that I have too much to tell and want to write it all down at once.
So, on Thursday, June 30th, we chartered a Vita 3 for the drive, because, as you already know, then groceries for the first few days, I still had to pick up pictures from Braunmüller, bathe, pack, eat, etc., so that we started punctually at 10 p.m. Inge helped me make sandwiches; by the way, she did end up going away with Inge, but she'll tell you about that herself. - Now I'm writing to you from my diary, which is just perfect, as I wrote in it every day, often while driving, after cooking, before going to sleep, or somewhere else.
June 30th, 10:15 p.m.: We drove off from 53 Spadina Rd, packed in as we were. Everything is in order except for: an increasing smell of gasoline in the trunk (Siegfried's, terrible), a pistol without a marksman, not-quite-perfect suitcases... the rest will reveal itself in time. Since I've already run around quite a bit today, I'll fall asleep soon; my head on Siegf.'s lap, and when I wake up, we are plunging into a gray haze for the first time. The gasoline here already costs 44 c/gallon. I go right back to sleep, because my stomach feels like a rock.

July 1st. It's only a quarter to 6 and I'm already up. So, now we've had supper. I made potato and bean salad with lots of onion, and served both with luncheon meat | peaches for dessert, which I got as a gift from the hospital. To drink, there's only Johnnie Walker, morning and night. But now, back to the diary.
We are in Cobalt on Lake Timiskaming, where we'll have a wonderful breakfast (pumpernickel, sausage, tomatoes, onion and mustard, the latter of which only I eat) and are in the best of moods. The lake glistens like Lake Constance - now I get to watch, Siegf. is already snorkeling (yuck!), but he drove wonderfully, otherwise I wouldn't have slept so well.
After driving for 6 1/2 hours (375 km) on bad roads that still call themselves 'Highway,' past forests in the morning, I'm tired again. - Shortly before Hearst, Siegfried pulls off again. When I wake up, there's nothing but forest around us, a sparse forest that, as I saw later, was ruined by a forest fire last year. All along the road there are signs like: "Use the ashtray, prevent fire," etc. At one very large spot, where the topmost branches on the trees were still green, a sign read: "this happened through carelessness." Between Hearst and Kinglac (135 miles) there is nothing on the map that would remind one of a village, and Siegfried really seemed to have forgotten to get gas in Hearst. But then, by great luck, there was a "Transcanada Lodge" with a gas station in the middle of the woods. In my joy, I wrote a poem:

The lodge was our rescue in our need,
for what for us both is bread
is for the "Class" (Chevrolet) the gasoline
and we wouldn't have made it much longer.

Since I drove again after Geraldton and Riggissee is running on its own, I pulled over shortly after next to a beautiful lake to cook and swim, so that Riggissee can get some proper sleep. The lakes here in Northern Ontario are magnificent, with forests, old logs pulled into the water by beavers, and rocks. You can tell that the area is barely populated; you hardly see any "Private Property" signs. In the small towns, there are mostly wood factories or sawmills, for example a huge one in Smooth Rock Falls and Geraldton. The lakes are full of logs. You have to be content with the roads; apart from a few spots, you can still drive 50-55 miles/h.
The weather is magnificent: wind, clouds, sun. - Now it's 10:15, and it's a good thing I'm letting him drive again, because he seems to be a bit snappy. The area here at Lake Nipigon is magnificent, the lake with the setting sun (that was a bit earlier) and the countless trees, with high, steep rock faces to the right and left in which caves seem to have their nests. The road is finally not straight for once, but wonderfully winding, and it goes up and down. In Pat-edthen we sleep in the car on a side street.
July 2nd. Set the clock back by 1 hour. We have driven 1125 km so far, completely without incident and through. The weather is wonderful again, the forest smells different than at home. After Pat-edthen, at a small lake, we had breakfast in the open air. At first it was a bit stiff. For breakfast we had: oatmeal, water and sugar. - From Pat-edthen to Kenora I'm driving again, it's no trouble, the lakes just don't stop. In Kenora, the last larger town in Northern Ontario, we stop to get the car greased and have the oil changed. Kenora is a nice town on the Lake of the Woods with many Indians (but respectable ones). Right after Kenora is the border to Manitoba, the smallest province in the West. Here we stopped again at a gas station in Winnipeg, where gas only costs 40c again. Winnipeg doesn't have many sights, it's quite old (but not beautifully old), with lots of terrible streetcars and flat, monotonous surroundings. Since it's not late yet, we also saw Portage la Prairie, the gateway to the prairie. There, in the middle of the prairie, it is an endlessly flat, green landscape, which promises good weather. (We were to find that out the next day.)
July 3rd. We left at 6 o'clock this morning. At first we wanted to swim in the lake, but a storm had raged quite a bit during the night. At first there were only puddles, but soon the whole road was covered with water. It was a magnificent area, like we were in a bird sanctuary, but Rigg. had his hands full making sure we didn't get stuck or slide off into the lake on the right or left. But when we finally got to the village on the beautiful lake, the entire yard was under water, so we couldn't get to the lake. That was a disappointment, since this was where the prairie began and the lakes ended. I was tempted to wash myself in a very muddy puddle, but I came out much dirtier. - We just got on the road to Saskatchewan, the roads are even nicer, just great, I'm always driving 60 M/h (96 km/h), which is easy to do with these cars, and especially because the roads are straight as an arrow and you can see for a long way. In Manitoba there were quite a lot of oil wells, here the grain elevators are starting, the landmarks of the prairie, which stand at every tiny train station. The weather is very hot again, a bit cooler than yesterday; because of the storm, many fields here are also quite flooded. - We're just driving through Regina, it doesn't seem to be a special city. In the afternoon we arrive in Saskatoon. Saskatoon on the South Saskatchewan River is the most beautiful Canadian city I've seen so far. (But that will change.) The city lies on the left and right of the river, with five beautiful, large bridges crossing it. In a magnificent park with illuminated fountains stands a castle-like hotel, it was wonderful. (But tons of mosquitoes.) We're spending the night here again.
July 4th. When we left Saskatoon this morning, it was quite cool, we're already pretty far north. By the time we get to the North Saskatchewan River, where we swim and have breakfast, the weather is lovely again. At the spot where I washed myself, there was a dead calf with its hide and everything, yuck! At 8 o'clock I started driving, because Rieffe always has rheumatism in his legs in the morning from sleeping. The roads are bad here again, and I usually get the worst stretches. At 12 o'clock in Lloydminster Rieffe took the wheel again. He usually likes to take over when I drive for so long, although it's going well. - We'll soon be in Edmonton, where Rieffe's friend lives, with whom he worked in Germany. Since we haven't washed with really fresh water for days, we are now desperately looking for a lake. The lakes shown on the map were all in swampland. So we drive 25 miles from Edmonton to Elk Island Park. We were just about to eat at a picnic spot that was completely empty, but since it had rained heavily during the night, and Rieffe is so good at getting stuck, we were soon deep in the mud. I'm just glad, Mother, that you reminded me about the shovel, because we really needed it here. I wrote in my diary:
1. When getting stuck in the mud, never put wood underneath, as it's incredibly slippery and the tires get hot. First, shovel some of the mud away so nothing splatters, then put stones under the wheels to provide a solid surface. Liegsp. didn't even have a tow rope with him, which left me speechless for a moment. If I had asked before the trip if he had a rope, he would have surely told me not to meddle in everything. - Well, the main thing is that we got out again, though we were ready for a bath. Here, too, you can only swim at a designated sandy beach; the other spots are too swampy. That also meant work with the laundry. It was such bad luck, because when we came out of the water, there were 5-6 leeches hanging on our legs, which are very hard to get off. That really gave me the shivers, and I was so looking forward to the lakes in Ontario.
Now we're heading back to Edmonton - to rest, get the car greased, and buy a wedding present. But since all the gas stations were closed, both plans fell through.
Evening in the car in Edmonton. The preparations and the futile effort to find a wedding gift were all for nothing, because Siggi's friend left on his honeymoon yesterday. Siggi is in a terrible mood, which I don't blame him for. Whether the money and time will last until Vancouver is too risky for us, plus we can't stop anywhere then, and that's not worth it. It's better this way, to really see the area of the national parks between Calgary, Banff, and Jasper. So tomorrow morning we're driving to Calgary, where Siggi also has a friend. - Edmonton is also on the North Saskatchewan River, and although the surroundings are also quite flat, the city is built up the slopes on the left and right of the river, which always looks nice. Edmonton is the fastest-growing city in Canada; it's the gateway to Canada's north and therefore unfortunately also attracts all the worst sorts of people. These are mostly old gold prospectors from Alaska who can't work in the winter, or other adventurers. Of course, the whole city doesn't consist of these people, but we saw them right on the main street, and I wouldn't have liked to spend the night there. By the way, Hugh's friend told us later that many people go to Northern Canada or Alaska in the summer to work in sawmills or gold mines. You can even go up there privately and try your luck, although 2/3 of it then goes to the government. In the winter, they come back to Edmonton and usually spend all their money again, because after half a year of that monotonous life, they want to live well again. But some also go up there because of the magnificent landscape, which is supposed to be unique. -
July 5th. I woke up at half past 10 in the morning to pouring rain and a bad weather forecast. The drive to Calgary is monotonous; I slept. Then we first looked for the friend's apartment. The streets are divided by numbers and cardinal directions, so it's easy to find your way around. For example, the friend lives at 2126 25A St. SW. We then had the car greased, washed, and the oil changed. Calgary makes a good impression right away, above all it's clean. There are villa districts here, well-bred cattle, and nice cowboys. - The car is just coming back from the garage, freshly washed. Hugh is in a great mood because of it; he loves his "Cleff" more than anything.
July 6th. The weather is magnificent, by the way yesterday it was nice too, and I'm in the best of spirits. Last night, Hugh, his friend Riez, his friend Dieter, and I were in town. They showed us the city, the city garden (zoo), and the petrified wood from the Rockies. Then we drove to a park where we rode the carousel and swung on the swings. It was a nice change of pace. Besides, the two of them are so nice; they are also well-rounded men, which you can't say about Hugh. The two of them, one 26, the other 27, live together in a nice basement apartment with a bedroom, living room, and kitchen. Each has his own car, a Ford and a Volkswagen. They are a carpenter and an electrician, and live nicely, about half an hour from Calgary. It was a matter of course that we slept at their place. In the morning, I was woken up by music that automatically starts 10 minutes before the alarm, which is just the right thing for me! - I wrote this in my diary there: If the Hofmann family ever moves to Canada, only Calgary would be an option, because it's the most similar to Germany with the Alps. The city (185,000) with its many beautiful single-story bungalows, the two rivers, Bow and Elbow, the forest-like park where you can camp, and most importantly, that you can be in the middle of the mountains in 2 hours by car. What Northern Germany is to Germany, Manitoba and Saskatchewan are to Canada (I've driven through them once), and Southern Germany corresponds to Alberta and B.C.
Right after Calgary you can already see the snow-covered mountains. I think I know what a feeling that was for me. The foothills and the mountains begin right away. At the park entrance, 5 miles before Banff, you are already surrounded by magnificent mountains. - In Banff, we first went to the mineral museum, the animal exhibit, and got some brochures about the area. By the way, you can also hire mountain guides here (but that's not for us, is it?). - We cooked our lunch at a very secluded spot on Lake Minnewanka; it's just as lonely and quiet here as in the Alps. Siegfried would have liked to fish in places that I thought were suitable, but since he's a city boy, that's not in his nature. - In the evening, we took a long walk through the forest, always uphill, away from all the tourists. One of the 2 hot sulfur springs is here, with a temperature of about 44°C. It stinks like rotten eggs and the rocks also have a yellow shimmer. Up above Banff, a bath has been made from it with a temperature of about 38°C. We went for a swim too, it's wonderful, but afterwards you're so exhausted that you just want to sleep. By the way, it's the best way to lose weight.
July 7th. The weather looks a bit worse this morning, but we're driving to Lake Louise anyway (80 miles). The drive is magnificent, even if a few high peaks are hidden in the clouds. At Lake Louise we park our car. It's quite cold. Then we walk along the lake, through the forest, always higher up, then over again, across rocks to the hanging glaciers. The whole thing is called a "Plain of Six Glaciers," which I like so much, do you remember from the Birkenkopf thing? It was still a bit different, you're much more directly up in the mountains. I think it's the air, too. The mountains made a powerful impression on him, even if he doesn't have much respect for their dangers, because he cheerfully scrambles up a brittle shale wall in sandals, not entirely free from giddiness. We had a cup of tea in the small teahouse. After 6 or 7 hours, we get back to our car and immediately looked for a place to cook, in a small forest clearing not far from the Chateau Lake Louise hotel. It was a nice spot, until suddenly a large, brown bear trotted past very close by. That was a bit too much for us, and we looked for another nice picnic spot. We have avoided these public places so far, but it's so nice there. There are open-air spots with 6 tables and a fireplace, where you can cook something, etc. Above all, you can stop there even when it's raining. Honestly, it's also quite cool outside, not like here where it's still 38°C in the evening. - He has finally realized that it's good if I don't buy bananas for 45c/lb, etc.
July 8th. Well, it's gotten quite late, but I couldn't get up earlier because I had such a stomach ache all night like never before, it was terrible. It's raining a little, we're driving to Jasper today. We would rather skip the Columbia Icefield, though we considered driving up, but the weather wasn't good enough for us. The mountains are quite high, up to 3800 m with a lot of snow and glaciers. Shortly after that, we see a mother bear playing with her little cub right in the middle of the road and take pictures. Feeding is strictly forbidden, because then the bears don't get enough and break car windows. As soon as you have a door or window open, they come in.
Now I'm sitting on a rock on the bank of the Athabasca River and have been waiting for a tow truck for a long time. The perfect but impractical eight-seater full of comfort-seekers drove as close as possible to the riverbank to eat. The main thing is that we're now heading into Jasper, albeit with almost no gas in the tank, no oil in the engine, and a half-broken spring. A cozy situation.
July 9th. It's 5:30 in the morning, magnificent weather, cold but wonderful, we're driving back to Banff today. Right after Jasper we saw another bear; they know that they find the most food near people. The drive is a pleasure, because all the peaks are clear. This time we're also driving up the Icefield, it's a magnificent feeling. - In Lake Louise we stop again at the picnic spot. Since it's only 5 o'clock, we make ourselves a pot of coffee and paddle a little way up the Bow River. It's magnificent here. The river is quite narrow, wild trees hang into the water, and you can just drift along beautifully under them. I know what a canoe looks like, it's pointed at the front and back and therefore tips quite easily, but it's more beautiful than anything else.
July 10th. Today we didn't get up until 8 o'clock, that's the latest so far. We meet Siegfried and Franke, who are both driving to the springs. We spend the day with them in Banff and at 5 o'clock we drive back together. We sleep in Calgary one last time and drive through the night. It's simply a magnificent night. In a small restaurant where we drink a milkshake (ice cream with milk), we heard the "Polka of the Fishermaid" (Fisherwoman from Lake Constance).
July 11th. Siegfried, Dieter, and I were at the Stampede parade this morning. It's a big, colorful parade, the same as all parades, except that here there's Western cavalry (cowboys), Indians, etc. Then we look at the Stampede fairgrounds. In the evening, I meet up with a few great girls and then we all went to the movies from Calgary, because it was already starting to rain as we were about to take the tourists to bed. Siegfried absolutely wants to leave right after the movie, so at 12 o'clock at night we say a sad farewell to our beloved Calgary. Quiet and wet. As a farewell gift, Dieter gave me negatives to enlarge, because you can't get German photo sizes in Calgary. Wasn't that clever of him?
July 12th. It rained pretty much all night, because when I wake up, we're in a ditch. The road is soft, and it's still raining. Riffgat hadn't pulled over far enough, because the outer edge (50 cm) of the roads here isn't paved, you can't see it in the rain. It was 5 o'clock in the morning, so we were lucky to get a tow truck in daylight to pull us out. The tow truck owner gave Riffg. a piece of his mind, because the speed limit on this construction stretch was 25, and he was definitely going 50. Now we're driving behind a truck; I don't think he'll speed anymore either. A road with construction sites, ditches, gravel, and mud began, because there was a lot of water on the roads from the ditches, and besides, it was pouring rain. After 3 hours Riffg. is driving again, the road is good, he's just annoyed that I drove off the bad road for so long, but I just have much more practice in this area. But after only half an hour the next construction site comes up, we'll see. The welcome sign is up to Halle. Because of him, and every truck has to wait 3 hours until the construction vehicles are done. I'll be glad if we even make it to Prague. Just as Riffg. had taken over the wheel for tomorrow, he notices that the clutch isn't working properly anymore. He yelled at me quite harshly that I had ruined it, but as I've now learned from expert circles, it can happen from all the water we drove through. It was perfectly fine again the next day.
July 13th: We slept in the car until Regina last night, though in a bad mood; the clutch had to be repaired, the cable couldn't handle the bad roads. We decided together that it would be better if the 135 miles without a workshop went well, because with the rain the road there will have gotten worse too. - Today we've already been driving for 6 hours, in the heaviest prairie rain that makes everything dark. In Digne, in the rain, we had the car greased and then inspected. Afterwards, the steering started to rattle very badly, you can hardly hold the steering wheel. Since it costs about 40 dollars, he thinks it will last until Toronto. He said I shouldn't worry Mom. We're spending the night in Genoa.
July 14th. So I'm driving off again with the broken steering and the completely worn-out speedometer. It's pouring rain and the morning sun is once again very sparse, which you can see quite clearly on me, because I haven't washed since Calgary. After breakfast, Hugh always likes to let me drive, and so now I'm driving through Northern Ontario again, that land of countless lakes, where raspberries and blueberries grow in the endless forests in huge quantities, and they couldn't taste any better. King was there to pick up mail, staying at the farm for Hugh for the time being, since he is going to Newmarket too early, because the post office is also very near the Superior (great lake). The area here and around Port Arthur is rocky right up to the huge lake. I drove for 8 hours today, it went pretty well.

July 15th. The sky is still overcast, but at least it's not raining, so I finally had a proper swim in a wide, empty lake. Tomorrow the journey continues. I drive through the simple landscape, which looked much more beautiful on the way here when the sun was shining. I drive to Longlac, where the Tomahawklersee is a bit further up. The road isn't paved, but it's not as dusty as before. Everything goes much faster than during the day, at least that's how it seems to me. The gentle rocking of the car doesn't make the old aches and the weariness of my limbs and body feel so powerful. Forests where the last big forest fire did its work (by the way, at one point there were 138 forest fires in Ontario), rocks with mountains, lakes with logs - little islands, water lilies, the forest usually goes right up to the shore, after the water lilies. After Cochrane, we drove another 240 km until 1 a.m. (Standard Time) to Cobalt, the place we left from on Friday morning. Night, fog, and rain. When I arrive, I'm dead tired, and feel correspondingly bad.
July 16th. The last day has dawned. As nice as it is, I'm looking forward to Toronto again, the club, and the people. In beautiful weather, we arrive in Toronto at 5 in the afternoon. It's maybe something to consider for later, to look at something a bit more western, then we would have had the time - the people. My address: 247 Franklin Ave, Toronto / Ont.

The trip is over, I can't quite process it. I have a completely different impression of Canada now, which is worth a lot. It was all very special, but the mountains were the nicest. I hope you can all imagine it somewhat, especially when you see the photos or maybe the camel hair blanket (?) that I'm bringing you, but not by airmail. Some of the color slides turned out nicely too, but it's too late now for you to see them, I'll show them to you in person. We'll see about the drive, if it works out. I'll write to you about it in the next letter. It's better if I start now. You're not missing anything.
I'm doing well, only I'm quite homesick for the pious ones, for Johannes, the berry harvest (?), chocolate, going to the movies, etc. - it's terribly stiff here. It's great in the car. At night, it's always 36°C, sometimes 38-39°C for hours. It's terrible, you can hardly do anything in the evening when you come into the room. By the way, in the whole house. On September 1st, because we need the court for tennis, especially with no roof below. But the heat is exhausting. Otherwise, I want to help diligently and not always postpone things, because I forget.
\end{document}
