\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersC L0006 (English)}
\noindent
Toronto, Feb. 2, 57

Dear Mom,
Thank you so much for your letter. I was very happy to receive it. It's nice that you got the pictures. Unfortunately, I couldn't send them by airmail, as that would have been more expensive than the pictures themselves. But of you, with Uschi there with you, I only have 4 pictures of Ari and one of each of you, but not from Bey's pictures. So I really hope that Uschi will send me some sometime. Inge is sending the ones from New Year's home, and you will then get them from Klausen's parents in Homburg and send them back here to Toronto via printed matter "photographs." That doesn't cost much. Uschi will have fun because of the group pictures.
That reminds me of something, which is why I'm writing right away before I forget again. You write that Christel's glasses make things look so much smaller. I know what that's like, as my glasses also used to make things look smaller, quite a lot in fact, since I'm -5.5. Of course, Christel's prescription is even stronger. But what I don't quite understand is why that would matter for a viewfinder picture. For someone who doesn't wear glasses, you'd think it would be bothersome, but when everything is equally small, you don't know any different, do you?
Well, before Christmas I had a new pair of glasses fitted, since I needed a spare pair anyway. My lenses have the same strength, but they have been ground a little extra to prevent eyestrain and... they don't make things look smaller anymore. I felt very silly for the first two or three days, since all the faces were so big and bulky, and 5¢ pieces looked like 50¢ pieces, and small, squarish oranges were nice and big, and I didn't know what was what anymore. I got used to it quickly and now I see things the same size with or without my glasses. Isn't that an option for Christel? My lenses aren't exactly simple either. By the way, over here you can get a regular eye exam for free, anytime, even without buying anything, just like you can get T.B. X-rays for free at any time, and now sometimes even for cancer.
The thing with Ursel and playing isn't very important to me; I only wrote that for her sake. I thought she might be bored. I also think that something like that is, of course, unimportant; you can't be constantly racking your brain over problems and have to do something "unimportant" once in a while. Hopefully she will get better, I wish that with all my heart.
I took the flash picture with a tripod, leaving the shutter open when the flash went off.
I still have so much from the trip. The other day I saw two movies that were both set on the same road I drove on. That is so interesting. I actually know North America better than Germany.
Warm regards from your
\end{document}
