\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersJ L0005 (English)}
\noindent
Toronto, Sept. 10, 54
Dear Michi,
You will probably be getting a small package from Photo Post in the near future with a lens for your Leica and a few filters. It's for one of our boys, Werner Kjär. You don't mind bringing it with you, do you? By the way, Werner gave a photography lecture on Saturday. We have 3 in the group who are fabulous photographers. I'm looking forward to my camera.
I'm always talking so much about the group, so I wanted to send you a picture from one of our outings in Woodview. In the group photo, everyone is a member except for the little one with the ball. From the left, the first one is the "Züngelchen" or "Gothic tongue," so called because he comes from Pforzheim and is the only one who speaks with a real non-German accent. He's on the board, our treasurer in fact. The one with the tie is Sigmund, our vice president; he's from Berlin and has 8 years in the Eastern Zone behind him. Next to him, grinning crookedly, is Joachim von Schwerin, our former president. He comes from the Pomeranian nobility and has now bought himself a farm. Good-natured and clumsy.
The girl in the chair with the glasses is Hilde Kochendörfer, a first-rate chess player, our secretary. The one in the plaid shirt is Horst, one of our youngest, an ethnic German from Transylvania. The one behind, wrapped in the blanket, is Werner, our chief optimist from Hamburg, who was unemployed all winter and yet always came cheerfully striding along with his violin. Next to him with the straw hat—Inge Kochendörfer, whom I've already told you so much about. And back there is Ellen, the pastor's daughter, a dear fellow.
In the other picture is Manfred, our president, in the middle of dancing swing with Peter. Manfred is from Hamburg, slick and very musical, a really decent guy, which is why he's our president.
My fountain pen is acting up again, please excuse me. Yesterday we celebrated the topping-out ceremony for the cabin we built in Uolna. That was fun. First the cabin was consecrated, the pastor gave a short speech, during which he fell off the keg. Afterwards there was a big feast. Sausages, potato salad, sandwiches, bacon rolls, cake, and beer. Afterwards we took a boat to the island, danced outdoors, one of our boys has
\end{document}
