\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersG L0006 (English)}
\noindent
Way 31st. mayen 3/4 7 ne! VI

Dear Mother, last night we kept our fingers from writing, so I'm finishing the letter now.
That business with the arrangement is a stupid story, how on earth did you get involved with it? Is the grocer not going to take anything more in the summer now? That is certainly a loss. I'll send you P 60 the day after tomorrow, because I'm completely out of debt with you, and I've been out of debt with you both for two weeks, which is a wonderful feeling. As soon as I can, I'll send you money, but in the next few weeks I'll need quite a bit for 3. C. I'll think about what the best thing to do is.
The ski area wasn't the only thing, but as I said, we had a decent run. Next winter we'll start skiing earlier. The gymnastics class was at the night school.
About the color film, it's terrible that for 24 DM nothing came of it. Who took those pictures? But do send me the Diola sometime, or what happened to the film, did the ones from Niagara Falls not turn out? 24 DM is an insane amount of money, even for me.
By the way, I'm not surprised that there was nothing on the other two films, because they were new. Those were actually black-and-white reversal films that I wanted to slip to the Cläfin, because I want to make color slides. All of this together is an expensive joke now, for which I'd at least like to have the film, because the falls were one of a kind back then.
The alarm clock works perfectly, I'm so glad I got it. Of course, I always put it pretty far away from the bed, but that way I get up and out of the feathers. If I don't, I just sleep right through it.
My watch, your very ad, is broken. I've taken it to the floor; hopefully I'll have it back soon.
Next Monday I have to go to the dentist. I broke a foot filling four weeks ago, which is a terrible mess. First of all, I would have stayed loyal to Dächle, and second, they are so outrageously expensive here.
I might buy myself an enlarger that I can also use to enlarge 6x6, because a good person I know bought a Rolleiflex. Then Siegfried, I've also already made passport photos; the other evening I have to take some portraits for an acquaintance for a few days.
So dear Mother, now I must hurry off to the hospital,

**Left margin (written vertically):**
I'll soon be taking Täfel-Dung again for the Opielien, tested by me, I also recommend it daily.
\end{document}
