\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS196o-61 L0006 (English)}
\noindent
Holland-America Line

R.M.S. Vancouver
Jan 4/62

Dear Ulla!

Your birthday is really inconvenient;
Christmas is barely over and it's already
too late to wish you a happy birthday.
But I'm sending you belated wishes for all
the best and that all your dreams come
true, as far as that's possible.
Please forgive me for the letter being late,
but I'm just very busy with wedding
preparations. I would have gladly stayed
home this last weekend, but duty is duty.
A few days ago I had a "shower." It's a
custom here for a friend to give you
a shower, either before a wedding
or before a birth. All the acquaintances
are invited, only women and girls;
men are not allowed at a shower.
Everyone brings something, and the
person the "shower" is for knows nothing
about it. Yesterday when I came in the door,
the light was out in the room and then
suddenly it went on and everyone yelled
"Surprise!" To be honest, I knew
about it beforehand, but of course
I had to act very surprised.

has, and only Karl his piano.
Then you pay for everything with a
check; it's not paid in cash at all,
often not even birthday cards
and mortgages, which is very
interesting. This weekend I was in
the Okanagan Valley, 300 miles
from here. That's the main fruit-
growing region of B.C. There are fruit
farms there, especially peaches and
apricots and plums, but also
many pears and apples and grapes.
The landscape looks completely dried
out; there's an almost subtropical
climate there in the summer.
Dry, everything is thirsty, cacti and
saltbushes are the only vegetation.
Rocks between the sandstone
and barren sandstone walls, grass
and yellow sand. Green patches are
the fruit farms, which are constantly
artificially irrigated. Pumps pump water
into the gardens, which are about 1 1/2
years old, and which are wide
above the ground. But in dry periods
the young ones are watered. In the
winter, however, it is very cold there,
often -20°. It has a terrible number
of rattlesnakes. In one town in one
summer. Otherwise, there are few
snakes in B.C. In Ontario, there are
also quite a few rattlesnakes, and
other poisonous ones.

Willing's parents want a boomerang
from Australia in the fall. Do you know
what a boomerang looks like? About
2 fingers wide and 60-70 cm long.
The natives in Australia use it for
killing; sometimes they throw one
around an opponent. In the tourist
version, it is thrown without the
killing and live part. But you have to
\end{document}
