\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersM L0006 (English)}
\noindent
Dear Mother,
How are you? I just wanted to
quickly write you the apple prices
at the wholesale market in
Frankfurt. We sold Corelli
for 48 and 50 pfennigs per pound
to small retailers, and from that
a rebate is still calculated.
The size is very
nice, though. Golden Pearmains are selling
sluggishly, 25 pfennigs, but much
worse than A-grade. There are also some
for 32 pfennigs. Boskoops cost only
20 to 25 pfennigs, but they aren't
particularly nice. We aren't selling
any Boskoops yet. In the city center,
varieties like the Cox
are now selling for 70 pfennigs. Apple prices are going up!
In general, people are saying
that apples will get expensive
in the spring. There are
also no foreign apples on
the market. Uli or similar
quality is so rare. Bodenstedt
ships a lot of fruit from here;
here at the market it is
not a popular buy.
Here in the newspaper, they are
also looking for girls for household
and farm work for Frankfurt. I
have now written to ask for more
detailed conditions.
I also recently wrote down
an address for Roslia. The Pelle in Backen-
Backen places ads in a Rauach
newspaper.
Several workers are
apparently being sought there. But
you, what are you going to do all alone?
Or should I rather
at the [?]
[?] I [?]
[?] the police [?]
a suitable manager
is found with the U.T.?
Do you actually intend to buy the
Packl Camol or Geyr-Urteil?
Best wishes, Dorli
Continued on
the next sheet!
Dorte Hofmeister
[?]
\end{document}
