\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersH L0001 (English)}
\noindent
Toronto, Dec. 14, 54

Dear Mother and little ones!
I wish you a very merry Christmas and nice, quiet holidays. But I'm sure you'll make it cozy for yourselves, you always do, although you will probably be missing someone more this time. Don't worry about her too much, she will settle in. The homesickness isn't so bad anymore; sometimes she comes home from work and realizes with surprise that she hasn't thought about home all day. That makes me happy, because it's a sure sign that she's starting to enjoy her work. Unfortunately, we don't get along very well yet; I clearly notice the difference between Germany and Canada. But what I notice even more is that she has never been away from home before, and that she had quite a lot of say in things there, whether it was at home, at school, or at the shop. That is, of course, very difficult for her. What is difficult for me is that I have to be considerate of someone again, that I have to wait for someone when I go out, or have to take others into account when planning my day. When you've lived a bachelor's life like that for three years, it's harder than you might think. Of course, Mechi can't know that, and that's why she often takes it the wrong way when I get impatient.
Besides, I really have picked up some of the Canadian pace. For example, on Wednesdays we go straight from work at 6 p.m. to gymnastics until 8, and by 8 o'clock we're already sitting in the symphony concert. Of course, it would be nicer to be freshly bathed, but that's just how it is here. The other day I got Mechi a free ticket, but she came home late and there was very little time left – and the theater was far away. She absolutely wanted to take a bath, but then it would have been too late. I had a date with Inge that evening, but then we went to buy an enlarger.
There's something else we think differently about. Mechi says and insists that she always acts just as she thinks and feels and according to her mood. She thinks I'm being "Canadian-sweet" when I'm friendly to our old folks, even if I don't particularly like them. But that's not being two-faced, as she so nicely puts it, but rather something that comes from being among strangers for 5 years and having to deal with people who weren't my type at all. And when you've moved as often as I have, you know what your dear housemates and landlords expect of you, and what they don't like to see. Mechi still has to learn that. But I will try my very best to make Christmas really cozy.
Mechi is very proud that she found her position at the hospital all by herself, although we had been there together once before, but nothing came of it. So I asked my head nurse if she could do something to get Mechi a position with us. She promised she would, even though it's not actually allowed for siblings and spouses to work together. But since then, she has been able to start at this position most amiably. That is, of course, wonderful for her.
Our record cabinet is very nice. Last time we listened to a symphony by Britten, the 1st Symphony by Brahms, and pieces by Moericke. Afterwards, a big surprise was announced, and everyone had to help with crafts, namely table decorations for our Christmas party. We made 20 trumpets, 20 angels, and many stars. Then all the tables were covered with blue paper and yellow stars were glued on. In and of itself, it would be nice to spend the whole Christmas evening in a small circle, but we planned this gathering for single people, those who have only been here a short time and really don't know where to go, who would otherwise sit at home in a cold room or go to a restaurant. We will have coffee and cake, we will sing and read a story aloud. Then we'll wash and rinse the dishes together, right! I'm getting Christmas off. It will be cozy.
We three—Inge, Hilde, and I—are sitting with the letters, of course, each taking turns while the others listen, right!
among your enlargements in the room, everything with the two of them and I'm pointing at a stool, we were only 6 people, but it was really very nice. The two of them are very much like my record club.
Excuse me, but what I sent was returned, now I have to make sure the package arrives on time.
is? Hopefully Tilde is big again? I had enough of that on vacation in August. Actually, everyone wanted to start. But then Inge did, and that's just how it was. Inge drew that. The flowers were not handmade.
\end{document}
