\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersM L0004 (English)}
\noindent
Hofheim, July 19, 1951

Dear Mother,

Well, the whole England thing is off now. Yesterday, news came from the Canadian Immigration Office in Karlsruhe. I'm getting a visa, and I have to go to Karlsruhe for a medical examination on the afternoon of August 17th. They wrote to me that German girls are very sought after over there, and they'll give me letters of recommendation here so that I can get a position right away. Just the day before yesterday, it said in our daily paper how warmly Germans are being received over there. You don't have anything against it, do you? You see, I had given up on it, which is why I made the arrangements for England. If you need me in a few years, I will certainly be happy to come back over. For the medical examination on August 17th, I have to bring an X-ray, a valid passport, and testimonials from three people vouching for my good character and honesty. Mr. Betzel can write one for me, but who else should I ask? And so I'll also need another declaration from you for a passport to Canada. Please send it to me as soon as possible. I'm sorry that I always have to bother you with this, but next year I'll be 21. Is Arlette there now?

Our new helper, who has been here for 3 days, is nothing special. He knows almost nothing about fruit growing. The girl is very nice and capable, but she isn't staying because she wants to go work for an American. There she'll earn 150 DM in addition to room and board. Hasn't Ursel found a position yet? On the one hand, it's good that she's still there. It's truly a shame that Dagmar had such bad luck. Has Erdmuthe ever written to you all? I'm going to write her a birthday letter later. Rüthe also has a birthday next week. She would surely be happy if Uschi or someone else wrote to her. We're starting on the Morello cherries now; we have quite a lot of them. I've only been swimming once.

Warm regards,
Dorle.

Uschi seems to have a lot to do as well; she hasn't written to me in ages.
\end{document}
