\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersM L0009 (English)}
\noindent
Dear Bärbel, How are you? How are your grades
at school? Have you improved? Will you be moving up to the next
grade at Easter? Here, the children in elementary school
don't have to do any homework, but they do have
school in the afternoons. I'm often alone with the two boys, and you
should see the things they get up to! If I knew more
English, I would tell them stories or read to them.
But I doubt that would be much of a treat
for them. So instead, we play football in the midst of silver
and crystal and chandeliers. That really makes me sweat.
The children have colds, you see, and have to stay
inside. The other day, 6-year-old Teddy got ahold of his mother's
nail polish and painted the radiator, the floor,
and his toenails. That gave me a few
hours of work afterward, because Mrs. Duggan loves nothing
more than top quality, and the cold. Today the children
went Christmas shopping with their mother.
Advent wasn't celebrated here at all, and they don't
know about Saint Nicholas either. I also haven't heard anyone
singing Christmas carols yet. The children do know
"Silent Night," and "Joy to the World." In Niagara Falls, there are 3
cheap days for shopping. The shop windows are decorated, but only
with artificial stuff and electric gadgets, but they do have
Christmas trees here, and holly branches too.
Bibbie is playing "Oh du lieber Augustin" on the piano.
Have a wonderful Christmas celebration. This year you
have plenty of space! Best wishes from Dorli.
\end{document}
