\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{L0006 (English)}
\noindent
We had, I think, 6-8 rowboats and one motorboat. You could already go swimming, too. There was just one big catch: the mosquitos. Uschi got badly bitten, as did everyone who hadn't experienced an early summer by the lakes before.
There was a guy with us, Heinz, who was fishing, and the blood was running down his face—no exaggeration. Uschi was still swollen for days afterward and was scratching like crazy. But they had announced on the radio beforehand that people should be careful and on no account go out without protective oil (but that stuff stinks worse than the fuel oil for the cows).
We took a lot of pictures. It was the first time I really snapped away with the new camera, so I mostly focused on landscapes, except for the "cover story" titled "Water Fight," which is a series of twelve pictures of a battle.
Two German films are just starting here in English: "The Last Prescription" with O.W. Fischer and "The Divided Heart" with Cornell Borchers, which is about an abandoned Yugoslavian child who is adopted by Germans and then, 8 years later, is demanded back by the Yugoslavian mother. Both sides are portrayed in such a way that you don't know whose side to take, so it's quite sad. Is the film "East of Eden" by John Steinbeck playing where you are yet? It's the best film I've seen so far, and it also features a completely newly discovered actor. Or have you seen "On the Waterfront" with Marlon Brando? Or "The Glass Slipper" with Leslie Caron?
Mechi is going to B.C. She's leaving on July 1st, which will be quite an experience; she'll write to you about it herself. She's going to take my Isolette for black and white photos and hers for color slides. Since I have my vacation at the exact same time, I can't very well give her mine, and besides, if she loses it or something else happens to it, hers is easier to pay for. Yesterday, Mechi was offered a great job as a photographer at the television station, \$40 a week, but she didn't take it because of B.C., which is something I wouldn't have done. She could have stopped working a little earlier next spring and then traveled to Europe via B.C. and California. At that job, she would have had every Sunday off and every other weekend from Friday to Tuesday. And that would have certainly been interesting work. She also thought that \$40 a week wasn't enough. That's an hourly wage of \$1.00, and I worked on the farm back then for 35¢ an hour and thought I was saving and earning a fortune. But that's Mechi's business.
Yes, Hilde and Mrs. Kochen are allowed to go back on July 1st. In Germany, Hilde went to business school, so in that respect, she's actually in her profession, whereas Inge went to textile school to become a textile technician and also spent half a year in Wiesbaden sewing and co-designing costumes and dresses for a film studio.
For Hilde, the transition won't be so drastic, since she'll be living in better circumstances in Germany than here; she's just dreading the long working hours.
\end{document}
