\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS1965 L0007 (English)}
\noindent
Banff, July 20, 65

Dear Mutti!

Thank you very much for your
letter from Westri, which was already
started there. That must not
seem all that long ago to you now.
But 4 weeks ago you wrote again
that you didn't get any cherries.
The weather? We just have so many
mosquitoes that one can hardly
was ideal for washing. Britt
contrary with a judgment.
boys people nearly Toy and
dusty car got covered in dust. On
the children of Mr. Ochs in
journey through America, and we
stay the night. We drove over the
with a right very far in Danube
from Germany. It is so, that
it is, and very unhealthy. Likewise
that Germany soon no longer
can. It also shows that Heinz
for the next 2-3 years in
America, that every house has a
In telephone numbers. Our local call
of which at the beginning of July in Vanc
In our station wagon a
boys we are expecting with great
There we experienced our first Christ
Christophen accompanies us on
is enough. If a fruit lies,
not. Also was a bit cautious

yesterday I received a
first letter. Hopefully
out soon and in the valley at
however, be over very quickly.
finally an end to so many
switch-overs. I did that because of the
can save. The weather was
I have constantly packed for the children.
Georg Calgary will with huge
clouds and we had a visitor from
Vancouver. He is on a 3-month
invited to join us
also into the mountains on Saturday. He
told, and he presented very interestingly
the labor problem is a catastrophe
so the increase in wages and prices,
with which Germany can compete
often experienced at the factories there are
what pleases me most is that
has a telephone, and how cheap it is,
weeks for 4 days. We had in the back
shady places to lie, and so they could
what they wanted, in peace, slept
the days, we also went swimming.
water until it was up to his nose
, until all the water to the heavens
, but he had a lot of fun doing it.
\end{document}
