\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS1962 L0001 (English)}
\noindent
Holland-America Line

R.M.S. Vancouver
Jan 4/62

Dear Ulla,
Your birthday is really impractical;
Christmas is barely over and it's already
too late to wish you a happy birthday.
But I wish you all the best belatedly
and that all your wishes come true,
as far as that's possible.
Please excuse the letter for being late,
but I'm just very busy
with the wedding preparations. I would
really like to stay home this last weekend,
but it might be mandatory. A few
days ago I had a "shower." It's a
custom here for a friend to give you
a shower, either before the wedding
or for a birthday. All the acquaintances
are invited, only women and
girls; men aren't allowed at
a shower. Everyone brings something,
and the person the "shower" is for doesn't know
anything about it. Yesterday when I came in the door,
the light was off in the room and then
all of a sudden it went on and everyone yelled
"Surprise." To be honest,
I knew about it beforehand, but of course
I had to act very surprised.

I received many towels, pot holders,
gloves, games, and all sorts of things.
Eric has already been living in the
new apartment for 2 weeks, but I haven't
decorated yet, haven't had the time.
Imagine, the first fifteen days are already
up for staying here. On New Year's it
was really like a madhouse.
At Christmas, the customers again
brought so much chocolate and perfume
and cigarettes and alcohol that we were all
completely sick. I've already given away two boxes
and still have 6 boxes sitting here.
Dear Ulla, now I haven't even
thanked you for the wonderful calendar
yet. I was so delighted with it.
How practical, too, that I can use the postcards
later. Thank you so much, you
made me very happy.
Since I'm very short on time, I will
write you more later. I wish you
once again, all the best and wonderful things for the
coming year. Your Uncle
I will send you another package after the wedding, but right now I just don't have the time

it wasn't enough
\end{document}
