\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS196o-61 L0010 (English)}
\noindent
R.M.S. Westerdam
Oct. 17/61.

Holland-America Line

Dearest Anni,
We've been away from home for 4 weeks now. I assume everything is going well for you, and how is everything? Are you still in day care? Or have you found something already? And received any information? When Frankfurt comes up, then the question again? That would be of great interest to you, the displays that are still inside because of the mess, to clear everything out. You will tidy it up once, and put everything back neatly, and whether you have work? or not? Darling? can't you empty the mailbox? and put it in the main post box? You will do that and it's done in no time, right? And I hope you get to your receptions. I can't say much yet, because it's still 10 days until we arrive, then I can write you more. I hope you are healthy and cheerful. Everything went very nicely here, we were already ready early in the morning at 6 am, by 10 o'clock we were in New York, and now we are traveling on to Montreal. I received a letter from your sister, they are doing well, and they have a nice apartment. I hope you are making good progress with your things, and if you need anything, then write me a letter.
Many greetings from all of us, and stay healthy.
Your Mother
\end{document}
