\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS196o-61 L0001 (English)}
\noindent
Vancouver, Aug. 20, 60

Dear Mother,

Today would have been Father's 61st birthday. I always think how much Father would have liked it here in Vancouver, with the mountains, the sea, and the forests. And the snow in winter. It is so much wilder and untamed here, not as cozy as in the Alps, but it has its own charm, which I think I would miss very much. A few weeks ago, we walked right into a black bear. We both stood still and looked at each other until the bear turned around and trotted away. Black bears are generally afraid of people, or at least they get out of their way if possible. You just have to be a bit more careful when they have cubs. Last week, there was another one in a suburb here; it came in through the kitchen door. The grizzly bears are more dangerous. They attack people more often and are also much bigger. We have seen grizzly tracks in the snow around the cottage that were 30 cm long and 20 cm wide. But they are rarer here. By the way, the black bears are often brown, too.

We go climbing so much now. When I come to Germany next year, I would like to do a good climbing tour with Uschi. Uschi must be quite good. We sometimes climb with pitons and rope ladders now, that is, only two or three rungs to stand in while hammering in pitons or on overhangs. I have the best climbing friends here, which makes it fun and gives you a feeling of security. We have also worked on the glacier several times, i.e., practicing your techniques, jumping, cutting steps, etc. I'm sure you will be very glad that you have Diesel. What about Christel then? Does she want to go to a school next year? Wilma and Edna would very likely come to Germany next year. When I am there, they could work for us. That would be nice for me too; we will have so much to tell each other. They are now on their way through the States to the East, after being in Alaska for 4 weeks. I miss Wilma very much; I was together with her every weekend for the last two years. Gudrun and George and Franki, my godson, are very likely going.
\end{document}
