\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersK L0001 (English)}
\noindent
Beaunsville, June 26th, '52

Dear Mother and Siblings,
It's about time I wrote to you all again. But you know best how it is in the summer; you don't have much desire to write in the evenings. Today, however, it's too hot to go out to sleep; we're currently averaging 96-97° Fahrenheit, which is 35-36°C. Quite nicely warm, I can tell you. My butter is liquid and the sausage stinks. By the way, that's why they salt the butter here, as it stays fresh much better. However, because of the many "Einer anderer" [one or the other], unsalted butter is also produced, but it's more expensive.

We are currently thinning peaches, which is keeping all the farmers pretty busy. The peaches are broken off to a spacing of about 4 inches (8-10 cm) and thrown down. Pridham doesn't have any strawberries; that harvest is almost over anyway, as a lot has dried up for those who didn't irrigate due to the drought. Pridham has his sprinklers running day and night. Since most of our plots are relatively close to the lake, a pump motor is set up on the shore, and the pipes are always laid out to the respective field.

Two weeks ago, we spent 6 days planting gladiolus bulbs, a vast field of them, which will then be sold as cut flowers. And we planted many, many roses. That must look beautiful when it all blooms. Sometimes in the morning, we drive up to 10 km to work, which is just a stone's throw around here. Next week the cherry harvest begins. We'll be working piece-rate then. You can make up to \$8 a day, which is 34 DM. There are so many sweet cherries here, but all on bush trees. There are sour cherries too, but not a lot of berry fruit. As a rule, they only keep the strawberry plants for one year after planting.

You should see how they spray here. All the orchards are laid out so that you can easily drive through them crosswise and lengthwise with the tractor. The tank is hung on the front of the tractor, and the whole pump apparatus is operated from the tractor. There's a device attached to the tank from which the spray comes out of 5 or 6 nozzles. You drive past each side of every row like that, and the whole spraying job is done by one man, sitting on the seat with a gas mask on. Since they are only bush trees or half-standards at most, everything really gets covered. They also spray very often; the spray schedules are announced on the radio. Every town here has its own radio station, which are mostly private companies that get their money from various firms and business people who, in return, advertise every 5 minutes for some chewing gum, hand cream, or car. In all of Canada, there are only a few state-run stations that get the radio license fee (\$2 a year, per house, because in our house, for example, there are 18 radios).

July 1st is "Dominion Day," the most important national holiday in Canada. The Dominion of Canada was founded on July 1st, 1867. There are other national holidays, like Queen Victoria's Birthday on May 24th, Queen Elizabeth's on June 2nd, and Labour Day on September 1st. These days are really celebrated; in contrast, I only realized it was Pentecost the day after it had passed.

The other evening I was in Niagara Falls and saw the illuminations, simply magnificent.

Did you actually get the money? Has Uschi sent the light meter yet?

Mrs. Bondy sends her kind regards. She wrote to me recently. Maybe she'll stop by here in early July and visit me. That would be nice. I'd like to visit her in the winter and want to go to New York at the same time, which isn't very far by local standards. The work on the bridge construction stops in December; I don't want to work here again next year either. I would prefer to go to British Columbia, where a lot of fruit and vegetables are also grown. The trip, 3500 miles (4500-5000 km), costs only \$63 by bus, though considerably more by train. You should see a third-class car here: upholstered seats like in a bus, a white cloth for your head, and when you press a button, the backrest reclines for you to lie down. The whole car is lined with leaden and silvery aluminum, with washrooms for men and women.

You must have a lot of work now. Are there apples this year? Liesel hasn't written to me in a long time. It's already very late, but still so hot that my face is all wet.

Now, my warmest greetings to you all from
Karl
\end{document}
