\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS1962 L0006 (English)}
\noindent
Banff, Dec. 26, 62

Dear Ursel,

Thank you so very much for the glove and shoe boxes,
and especially for the lovely table. That's really practical.
I can imagine that you also need something on the armrests
when a little one is starting to eat by themselves and
paws around in their plate. Thank you so, so much. I have
truly received everything I need from you all. From
Gisel, I got a very nice little knitted cardigan and cap.
It was surely quieter and calmer than usual for you
at Christmas. We had a nice celebration as well. It's
fun to decorate a Christmas tree and to think about
how to spend the evening and what to cook. The
cooking is a lot of fun for me now that I'm no longer working,
and especially using up leftovers—that's even more
fun for me than making something new, since you have to
use your brain a bit to whip up something that doesn't
taste like leftovers. I also made a gingerbread house
for the three-year-old daughter of Eric's boss. No
one had ever seen a gingerbread house, except maybe
in pictures, and they all thought it was sweet. Here it is always
sunny, and the skiers are eagerly waiting for more snow.
While the eastern part of America has a lot of snow and cold,
the west is very mild with little snow, and the
winter sports areas are complaining a lot about the loss of guests.
Very warm greetings and good wishes for the New Year,
Your Dack - Eric.
\end{document}
