\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersJ L0006 (English)}
\noindent
the season began yesterday. Spring
arrived again overnight, so to speak.
In Niagara Falls, the apricots and cherries were
already blooming last Sunday, and
by next Sunday, everything will be in bloom.
But first, I want to thank you for your
lovely birthday present.
The package arrived on April 28th. The
blanket is just beautiful, and the pillow
too. The room looks so much warmer
right away. Thank you so much for that. You
hardly ever see anything like it here. When Mecki
comes, I can make it nice and cozy.
It already is, actually. I already have a whole
shelf full of books. All the ones from you all,
then a 20-volume lexicon. And the day before
yesterday I was at the big garden
show, and there I subscribed to three
magazines, "American Camera,"
"Canadian Homes and Gardens," and "McLeans,"
a family magazine, and illustrated.
For that, I got three books for free.
One is a lexicon with an atlas, with separate
sections for the English language, law, legislation,
Greek history, and more. You can find something
about everything in it, a huge book. The
second is a home medical guide, which you can
always use; the third is
a book that contains 101 books—novels,
plays, speeches, biographies—in condensed
form. It has Plato and Homer,
Aristotle, Goethe, Marx, Dante, Shakespeare,
and others. It's really very good.
Have you heard anything from Mrs. Bondy?
Once, two years ago, she wanted to
visit me in Beamsville, but that
apparently didn't work out. I'll probably send
another card at Christmas, but nothing
more. It looks as if I wanted her
help, at least that's how it seems to me. If
I can get into the States, I'll visit her.
Elly Graeffe's brother
has a business here. I went there once,
but no one was home.
I will probably stay in Toronto at the
hospital this summer. One reason is that
I'd like to be here in the winter, since
it's easier for me to find something here.
I really enjoy the work, and I've settled in
very well. I'm doing the same work as
the certified dietitians, and of course,
that's a lot of fun. On Friday, I'm invited to the
graduation ball, which is a
great honor, even outside of
work. To be honest, I don't really
want to go, because it's all "formal,"
which means you have to show up in an evening
gown and the men in tails. We'll
see if I can borrow one somewhere. My finances
are just not too good, since I just
got rid of \$90 at the dentist. It's
really nice when you're at home
and get that paid for. But that would be
saving money in the wrong place. I now
brush my teeth immediately after every meal
(I used to only do it in the morning and
evening). But you have to do that here because
the food is softer, more sweets, etc.
By the way, the chocolate was wonderful.
I have never owned so much chocolate
at once. And the letter-shaped cookies
remind one of the old days at home. That
must have been a long time ago, during the war

I'll send my birthday wishes along later. Your Karl.
\end{document}
