\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersB L0003 (English)}
\noindent
Toronto, May 19, '58

Dear Mother!

Thank you very much for your letter. Since you're asking about birthday wishes, I wanted to write back right away. I would be very happy to get an ever-ready camera case, preferably one where you can screw the tripod in at the bottom. Or, perhaps, craft supplies or magazines, or a pair of shoes, preferably black. Suede shoes, like the ones you've sent me before, I think I'm a size 3 to 3 1/2. But otherwise, I'd be happy with anything.

Inge had her birthday yesterday, we had a nice celebration. We're often digging again at the university for a performance, this time with Kenley Beilton and Tony Baurand, which is fun.
Today at the bank, we caught a fraudster. He had cashed a bad check for \$250, did it today, and wanted to pick up the money the next day. We weren't sure, and neither was Elke, whether the check was real, since it came from out of the country, or if it would come back as bad. We called the police right away and they came and got the guy. I was supposed to be called as a witness, but I don't know what came of it, but we did recognize him again. He had talked a lot, and then he brought in a check for his account for \$250.-- The next day he wanted to withdraw the money, but I didn't give it to him, since I didn't know yet if the check was good. And two days later the check did in fact come back, it was a false name. We called the police right away, I had to describe the man, which is very hard, what do I know about how much the man weighs, or what kind of ears he has. But they got him soon after. He had tried the same thing at other banks as he did at ours and had even succeeded in getting the money.

Last Sunday we were in Leamington near Windsor to perform in a play, it went very well. We also had glorious weather and drove to a national park near Point Pelee Park, a peninsula in Lake Erie. We spent half the day sitting outside there, the peace and quiet were really wonderfully nice.
Do you have an Easter holiday now? You all don't, I think, but do the workers get time off? Unemployment is still very high. Older people can't find any work at all. Up here in Vancouver, there are fathers with 4 and 5 children who are unemployed.

Again, wishing everyone a happy Easter, and thank you all again very much for your letter and the pictures.
Your soon-to-be Uncle

The boy tried to get it with force and cunning, but we stood firm.
\end{document}
