\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersH L0005 (English)}
\noindent
Toronto, Oct. 18, 54.

Dear Mom,
Thank you very much for your long letter. I was very happy to receive it. The letter that said you bought a device—just before Christmas, I can't think of what to get for you. Does Gerd have a device now? I'm looking forward to getting my Katina. I thank you for the offer you made me for the \$200 you'll get from the money. Do you have it already? I hope so. You're going to spoil me, I'm sure of it.

We had records once, but we couldn't... We are now also members of a club that sends us 12 records a month. We meet at one of our places or go to a café and listen to the music. John is originally from... all the science subjects like math, chemistry, biology. Almost everyone here goes to night school, even many housewives. You should have seen it on the first evening of registration. There were no fewer than 3500 people. And that's just one of several night schools.

On Friday evening, we had a hurricane here. It was interesting to experience something like that, although it's very sad. Over 100 people died here in Toronto! The damage here alone is many millions of dollars. The hurricane, "Hazel," had been announced all afternoon. It came all the way from Mexico, having already passed through the U.S.A.

The hurricane was forecast for 7:30. At 4 o'clock it started pouring, and a little later... The wind wasn't too strong yet. It rained steadily until 9 o'clock, always just as hard. The ground became saturated from the rain. I finished work at 7 o'clock and started driving. It took me 1 1/2 hours! The water was standing on the street. Large potholes were on the roads that you couldn't see. We have two rivers in Toronto, one in the west, one in the east. Both had several bridges torn away.

Many houses were swept away by the water because the rain had softened the ground, so they were washed away for miles. The families were still inside the houses. In the morning, they rescued people from trees and roofs. The Holland Marsh, a very fertile area north of Toronto, is completely underwater, since the highway, which is slightly elevated, acted like a dam and held everything back. All roads out of the city were closed for 3 days; water and electricity were out. On the lake, houses were floating with trees carried out on top of them. If you haven't seen something like that, you can't even imagine it.

Did you know that hurricanes have girls' names? The first one of the year starts with A, so Adele, for example, the second Ben, Sara; this was the 5th, so it started with an H.

Now it's slowly turning to winter. It already snowed 4 weeks ago in northern Ontario. In 3 weeks we'll send everything off. This year I will try very hard to be home for Christmas, but don't tell... because it will come. We'll bake... Christmas in a foreign country... Then, she'll probably have to work, but maybe she'll come earlier, around the same day.

Two weeks ago, all the night schools started again. Inge and I signed up for a class, but it's overcrowded, so we have to wait for 4 weeks. We did woodcarving, which we thought was great fun. We also have gymnastics with music once a week. It's an old Czech teacher who really... She asked us on the very first evening if we'd like to be in a performance.

Inge and I, if we'd like to take English at a school. It's \$5 for the whole semester, and for that you can come every evening and take different courses. We'll see. There's nothing you can't do: cooking, baking, sewing, painting, drawing, bible studies, spelling, photography, artful knitting, from soloists to...

Best wishes,
Your Lotte.
\end{document}
