\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersK L0002 (English)}
\noindent
Beamsville, August 3rd

Dear Folks!
How are you all doing? Hopefully
you are all healthy and not working
too long. How is the harvest? Now
you'll already be harvesting apples and
pears. Are the young peach trees bearing fruit yet?
Here the peach harvest is now really
getting started, which is the main crop. Everything
is sorted very well, and anything that doesn't
reach a certain size (which is quite large!)
is thrown away, as it cannot and may not
be sold. The
stores are only allowed to sell inspected and
sorted goods, and farmers' markets
only exist in very few
cities. So it's important that everyone
thins out their crop and sprays, prunes, and
fertilizes well. It's the same for the cherries, strawberries, and
all the fruit. This year,
however, the strawberries were all
very small, for those who hadn't watered,
so most of them went to the canning
factories. Most of the sour cherries
are picked without stems for
the factories. But it's cheap, so that
every farmer already 4 weeks before the seriousness now himself must after a
watch-night, and then it is precisely determined
how much he can bring each day,
whether it rains or whether he is not allowed to be
hungry, whether the cherries open,
he fordet not loose, to on the rest hardly
a pack not on the tree leave.
so he is no longer master

so here is the danger, the addiction grabs
brings the nation, every train station,
is here a fruit receiving station, an inspec-
tor checks every cartload (spot checks), and
woe betide if there's been any shoddy work. Then
the farmer has to pay 860 Marks and
has to sort through the entire load
once more. Some farmers had their sacks
demand after rain, if they danger
was, exactly 10 claps the cherries
re-sort by color, white were the
olen dust. As soon as the last cherry
is gone, the cherry trees must immediately
be sprayed against the
plant that the ears also very
tends to affect 3 against is, and even the
must the lowest branches
with poisonous substance, that always with
every poisonous substance, that always with
\end{document}
