\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersA L0006 (English)}
\noindent
Vancouver, Dec. 14, 59
1959

Dear Mother,
For Christmas, I wish
you all the best. Will Medi
and Bärbel be with you? How much
you all will need the holidays!
How far along are you with the work?
I wonder how that will be next year?
But now at Christmastime,
one shouldn't worry so much.
How is Ursel? Do you have an address
for Liesel there in Stetten? Other than a few
postcards from the summer, I haven't
heard from her since Easter. I couldn't
even write to her for her birthday.
My vacation in Toronto was very
eventful. My drive was wonderful,
even though I was alone. The most beautiful
experience was Yellowstone Park
with its boiling geysers and
springs. The best part was that
I had the whole park to myself,
because it had officially been closed since October.
I asked a park ranger,
and he gave me permission to drive
through. In August, there had been a very strong earthquake there, which had
buried entire valleys and canyons.
In some places the pavement of the road
had burst open, and boiling
water was coming out right from the
middle of the road. There is a
geyser called "Old Faithful" that
spouts water at regular intervals
of one hour, over 100 feet
high. In total, there are over 3000 geysers
and hot springs in the park, which is about
2500 meters above sea level.
The whole park bubbles and boils and
steams and hisses. There is a mountain
that rumbles and rumbles so loudly that
you can hardly understand anything, and steam
comes out of all the cracks.
Some springs are a warm pulp
of sulfur or copper that comes
boiling out of the earth. The day
was very cold, snow lay on the
road and in the forest, and through the
frosty landscape flows a stream that
looks like an ordinary little forest
brook, clear water, but as hot

as a cozy bath. In the park there
are very many bears and buffalo and
elk and moose, which are all very wild,
and many tourists are attacked by the bears
alone every year because they aren't
careful.
In Toronto, everything was then a bit
tight on time. I arrived on Friday evening,
and on Sunday was the baptism
of Ursel Schnell, for whom I am the god-
mother. Afterwards, there was a big
youth group reunion at Sigmund
and Ellen Steiner's. All the old friends
were together, and 4 babies
were already there with them.
The week then went by quickly
with visits and parties, and on
Saturday and Sunday we were still
at the N.Y.is and Clausen's cottage. I
slept in the car again on the way
home, even though it was as cold as -20 degrees Celsius.
Now we are skiing a lot again,
there's already over 1 1/2 meters of snow here
at Baker, where we always go.
At Christmas we also want to go ski...
\end{document}
