\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DORLELETTERS196o-61 L0004 (English)}
\noindent
R.M.S. Maasdam
.................................... Nov. 3/61

Dear Mother!

Today is already the 3rd of November, and I've already been back here for almost a month. How time flies. Were you in Rütte for All Saints' Day? Was Christel at the Deutschs'? Has she had her vacation already? Are you still going to the market? If I hadn't been needed, I would only be leaving now. I would have gladly helped out longer, and I enjoyed the work. I wouldn't have believed it myself, but it was nice. Nevertheless, everything here went back to how it was before, and I'm enjoying my bank work again. Eric was of course overjoyed that I showed up so unexpectedly a month early. Over the summer, he built a very compact setup in his VW bus: two box beds, a sideboard, a table, and 8 cabinets, one for hanging clothes. We tried camping in it last week as a test, it was wonderful, and you have a lot of space and it's nice and warm, even with below-freezing temperatures outside. So when we go skiing somewhere else, we can always stay in the VW, which saves a lot of money. At Mt. Baker we don't need to, of course. Eric is giving ski lessons again and I'm working on the ski patrol. We already have a lot to do.

Now at the beginning of the holidays there are many broken bones, which we transport down on the sleds. Oh, I wouldn't want to lie in one of those sleds, not even without broken bones. The poor things, sometimes on steep slopes it happens that it's just a straight slide down, and you can't brake anymore. Often we see the sleds racing down from the very top. You could hear some real screaming from them then.

So, now I have to go to bed, it's already late.

Warmest greetings, also to Ursel and Uli.
from Karl.
\end{document}
