\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{DorleLettersC L0011 (English)}
\noindent
Hopefully the package arrived on time. We're sending it late again, as always. For the reception, did I include the pictures of the escape for you, or did I only mail them today? I don't have the date because I wasn't fully recovered yet. I just didn't want to disappear without any news. Regarding what you ordered for the time, has the paper or the bread from D.B. arrived? I'm a member now. I had a letter for you with it. But your brother-in-law mailed it because he isn't coming, so you will receive it from him. I am prepared to pay the 510 francs, I would just like to know, would you prefer if I stay there longer out of my own free will. I had planned to go to Felsen for 3-4 weeks next April, but now I will probably take a 4-week spa stay instead, but I want to go away to Alaska before then. Maybe I'll get a portion of it after Alaska, because I only get paid vacation next year. For what I receive, 2 months' worth is credited to me.

us if you could take me with you to Alaska? Shall we call France to see if she has ever flown? From the 25th on we have no money without working, if they don't give us work, don't let us wake up, if she wants what comes out of it for us.

Warm Christmas and New Year's greetings
from your Karl
\end{document}
