\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\begin{document}
\section*{L0009 (English)}
\noindent
were, and everyone really enjoyed the outing again. In the evening, however, we had to be back by 8 o'clock for the club, where we heard a highly interesting lecture on the influence of world history on the church. A good speaker can make even the most boring topic interesting.

Inge and Klaus are at the club more often again now; Klaus likes it with us. I'm still there quite often, though of course not as much as I used to be. Inge is going to gymnastics again, but naturally she has more to do with the household now. Klaus is an electrical engineer and has a job as a technical draftsman. Imagine, 8 days before the wedding, his sister and his cousin were tragically killed in an accident in Germany. That's why we kept the wedding so small. The ceremony was at 10:30 in the morning and was really very nice; Dr. Gögginger does a lovely job. Manfred and I were the witnesses. Otherwise, besides the pastor's wife, no one else was in the church, since the youth group was away on a trip. Then we had the wedding meal, potato salad and schnitzel, and then all sorts of little "appetizers." I had baked a beautiful buttercream torte, decorated with piped roses and pansies. The youth group had given Inge a lovely tea service, which was put to use right away. Then we set off for Woodview, where the two of them are staying, and Manfred and I drove on. That was quite a nice drive, over 300 miles (480 km); we arrived at the others' place in Baysville at half past 11 at night.

Inge's sister Hilde is doing well in Germany. She isn't working yet, but will soon start at an American office in Wiesbaden. She spent the whole summer traveling with her father, in Holland and Belgium and in Italy.

Our new apartment is very nice; we have more space now, but we also have correspondingly more visitors. Sometimes half the group is here. You ask about Christmas wishes. I would really like a ski anorak with a hood, preferably blue. Or else a good camping stove. For smaller things, I'd like a case for filters and a lens hood that attaches to the strap, or a washbag.

I'd like to wish you and your parents a very merry Christmas, and a good, happy New Year. Warm greetings from all of us.
\end{document}
